### 2023-06-08 full-paper/template/manuscript.tex
tex(template): add default template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template revision history:
% BS2023: Revised by Yikun Yang, ian@tongji.edu.cn
% BS2021: Revised by Filip Jorissen, filip.jorissen@kuleuven.be
% BS2019: Revised by Alessandro Prada, alessandro.prada@unitn.it
% BS2017: Initial version by Michael Wetter, mwetter@lbl.gov
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twocolumn, a4paper,10pt]{article}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
columnsep=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{boxedminipage}
\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[font=it]{caption}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{3pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
%\renewcommand{\baselinestretch}{0.7}
% FOR enumerates
\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
\setenumerate{leftmargin=*}
\setcounter{secnumdepth}{-1}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Paper Preparation Guide and Submission Instructions for\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
\vspace{4pt}
Building Simulation 2023 Conference} 																																% Line 2 
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
Jane Doe$^1$, Richard Roe$^2$, John Stiles$^2$\\ 																										% Line 4
$^1$Institution 1, City 1, Country 1\\ 																																	% Line 5
$^2$Institution 2, City 2, Country 2\\ 																																	% Line 6
% comment the lines below and add \phantom{} lines as needed to reach a total of 10 lines
\textit{(The names and affiliations SHOULD NOT be included in the draft submitted for review)}\\ 			 			  	% Line 7
\textit{(leave blank up to line 10 - remove line numbering from final version)}\\ 															% Line 8
\phantom{Line 9}} 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
This document explains how to prepare a paper for submission to the Building Simulation 2023 Conference. It also includes the instructions for submission and some other information. This file can also be used as a template if you are using MS-Word. In this case you can use the preselected styles in the Style Gallery to format the document.

\section*{Highlights}
\begin{itemize}
\item Extended bullet points in place of the keywords
\item Lay emphasis on your novel methods and results
\item Reach a wider audience with practical implications
\item Three to five. Keep it short and precise
\end{itemize}

\section*{Introduction}
The paper should be prepared in A4 size, portrait oriented, with 25 mm margins at top and bottom, and 20 mm margins at left and right. Use font type Times (Times New Roman) for the entire document with different style at different part of the paper, as explained later. The \textbf{maximum number of pages is 8}. Please \textbf{\underline{do not}} add page numbers, headers or footers.\\
The paper includes 2 sections (top section and main body) and different parts. Mandatory - in bold - and optional (recommended but not limited to) parts are:\\
Top section
\begin{itemize}
\item \textbf{Title}
\item \textbf{Authors}
\item \textbf{Authors' affiliations}
\end{itemize}
Main body
\begin{itemize}
\item \textbf{Abstract}
\item \textbf{Highlights}
\item \textbf{Introduction}
\item Methods
\item Results
\item Discussion
\item \textbf{Conclusion}
\item Acknowledgments
\item Nomenclature
\item \textbf{References}
\end{itemize}
Optional parts can be replaced according to the needs but the order should be preserved.\\
Second level paragraphs are acceptable. Lower level paragraphs are discouraged.\\
Do not leave empty lines between titles, paragraphs and figures in the main body. Use paragraph spacing above and below titles and paragraphs as specified in the following. \\
In case you use MS-Word, you can refer to the predefined styles in the gallery included in the MS-word template (in alphabetical order):
\begin{itemize}
\item Authors
\item Captions
\item Equation
\item Figure
\item List (bulleted)
\item List (numbered)
\item Heading 1
\item Heading 2
\item Normal
\item Reference
\item Tables
\item Title
\end{itemize}

%---------------------------------------------------------------------------------------
\section*{Parts of the paper: top section}
%---------------------------------------------------------------------------------------

The top section of the first page of the paper is used for the title of the paper, list of authors, and authors' affiliation. This section always consists of 10 lines of exactly 14 points spacing, in single column format.
\subsection*{Title, authors, and authors' affiliations}
Titles (MS-word: select \textit{Title style}) should be in bold font size 12 points. Do not use more than 2 lines for the title, and try to limit it to ten words.\\
Authors (MS-word: select \textit{Authors style}), authors' affiliations, and other information should be in font size 12 points. In case of more than one affiliation, reference superscripts after the author's names and before the corresponding affiliation will be added.\\
Authors' affiliations (MS-word: \textit{always in Authors style}), can include contact (e-mails, telephone numbers, postal address, etc.) and other information. However, the 10 lines limitation applies. If you need less than 10 lines for all the information, please leave the remaining lines blank.

%---------------------------------------------------------------------------------------
\section*{Main body}
%---------------------------------------------------------------------------------------

After the 10 lines in the top section, the rest of the document is in two-column format, with a space between the two columns of 8 mm. The space between the columns should be centred on the paper. Line spacing is exactly 12 points.\\
The main text should be typed in 10 point font, justified, with 3 points spacing below each paragraph (\textit{MS-word: select \textit{Normal style}}).\\
The headings of each section should use font size of 12 point, capitalized, with 3 and 3 points spacing above and below (\textit{MS-word: select \textit{Heading 1 style}}). The headings of the subsection should use 10 points size and bold, with 3 points spacing below (\textit{MS-word: select \textit{Heading 2 style}}). Left alignment is used for headings. Both the sections and subsections \underline{\textbf{should not}} be numbered.

%---------------------------------------------------------------------------------------
\subsection*{Abstract}
%---------------------------------------------------------------------------------------

The abstract of your paper should be about 100 words.\\
Abstracts must clearly identify (i) what is the current state of the art, (ii) what are its deficiencies, (iii) what methods have been applied, (iv) what are the results, and (v) what is the lasting contribution of the submission.

%---------------------------------------------------------------------------------------
\subsection*{Highlights}
%---------------------------------------------------------------------------------------

In 3-5 bullet points, with short and precise sentences, highlight where this paper moves beyond the state of the art and what a simulation practitioner should take away from your work: always do A; avoid B; consider C and beware of D in case of E.

%---------------------------------------------------------------------------------------
\subsection*{Figures and Tables}
%---------------------------------------------------------------------------------------

Figures and Tables are preferably included in the text where they are discussed rather than at the end of the paper. In the case of figures, select the ''In line with text'' from the layout options if you use MS-Word. A centred alignment with 3 and 3 points spacing above and below is required (\textit{MS-word: select \textit{Figure style}}). \\
Both figures and tables must have a number and caption. Figure~\ref{fig:fig01} (\textit{refer this way to a figure in the text, do not use Fig. ~\ref{fig:fig01} or figure ~\ref{fig:fig01}}) is an example of a graph in the text. Captions (\textit{MS-word: use \textit{Captions style}}) always follow the figure in italic font size 10 points, and centred, with 3 and 3 points spacing above and below.\\
If figures authorship does not belong to one of the authors, authors are required to ask to the copyright owner the permission to use that material and to provide a proof that the permission has been accorded.\\
Colour images are welcome.\\

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{img/fig1}
  \caption{A gentle reminder.}
  \label{fig:fig01}
\vspace{-16pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{figure}

Table \ref{tab:tab01} shows an example of a table, where the caption should be on the top of the table, with the same format as figure captions. Text in tables can be in font size of 9 points and centred, with no spacing above and below (MS-word: use \textit{Tables style}).

\begin{table}[ht]
\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\caption{Example of a table.}
\label{tab:tab01}
\centering
\begin{tabular}{| c | c | c | }
  \hline
  \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
  \hline
  Entry 1 & Entry 2 & Entry 3 \\
  \hline
\end{tabular}
\vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table}

Oversized figures and tables may be included in the text. However, authors may arrange the layout properly so that it appears at the top or the bottom of the page, or preferably on a separate page at the end of the paper. Figure ~\ref{fig:fig02} is an example of an oversized figure.

%---------------------------------------------------------------------------------------
\subsection*{Equations and units}
%---------------------------------------------------------------------------------------

Each significant equation or formula should be displayed on a separate line. Center equations and place consecutive equation numbers flush right in parentheses. For example,
\begin{equation}\label{eq:example}
  a^2+b^2=c^2.
\end{equation}
If you use MS-Word, use the Equation style and use tabs to position equations and equation numbers correctly.
Mathematical symbols should be clear and avoid ambiguities. Keep using font size 10 points. Symbols representing physical quantities (or variables) are italic. Symbols representing units, operators, labels and numbers, are regular (upright).\\
Equations should be referenced in the text by their number (\ref{eq:example}). A brief description of the symbols used in your paper should be added in a nomenclature section at the end of the text or inline with the text where the symbols are first used.\\
SI units of measurement are mandatory. If other units are mentioned, always provide their equivalent value according to SI.\\
SI notation must be adopted as regards symbols, prefixes and other writing rules. In particular comma as a decimal separator is preferred to the point (which is anyhow allowed if used consistently throughout the manuscript). If needed, only blank spaces are allowed as thousand separators.

%---------------------------------------------------------------------------------------
\subsection*{References}
%---------------------------------------------------------------------------------------

All publications cited in the text should be listed at the end of the Main body in a References section, in alphabetical order of the family name of the first author. From the second line on, each entry should be indented by 5 mm. Justified alignment with 3 and 3 points spacing above and below each paragraph must be used (\textit{MS-word: select \textit{Reference style}}). Examples of reference style are reported in the reference section below for journals, conference proceedings, books and technical standards.\\
In the main text, refer to a reference using author-year style such as \citet{Clarke2015:1} or \citet{ChuMajumdar2012}. When the reference is not a part of the sentence, use the author-year style in brackets (\cite{Clarke2015:1, ChuMajumdar2012,Monarim2014, BSDO2011, Mahdavi2011,iso52017}).

%---------------------------------------------------------------------------------------
\subsection*{Bulleted and numbered lists}
%---------------------------------------------------------------------------------------

Numbered and bulleted lists must be justified, with no indentation, and 5 mm hanging. You may use List (bulleted) or List (Numbered) styles in MS-Word.

%---------------------------------------------------------------------------------------
\section*{If you use MS-Word}
%---------------------------------------------------------------------------------------

You can use the .docx document as a template if you use MS-Word. Please use the style for each section as has been defined in the template. You can either use the template, rename it, and cut-and-paste your paper from other document(s) into the template, or you can use your document, open style organizer (Alt+F8 to open the Macros window then click the Organizer button for the Style tab), delete all your styles and import the styles from the template.
If you use the template, do not forget to disable the line number on the Top section of the first page before you submit the paper and cancel instructions comments (\textit{in brackets and italic fonts}).

%---------------------------------------------------------------------------------------
\section*{If you use \LaTeX{}}
%---------------------------------------------------------------------------------------

Please use the \LaTeX{} template you can download from the conference website. In the compressed folder, you will find:
\begin{itemize}
\item \textbf{format.tex}: a fill-in form for a standard article with usage comments. Please copy it to a new file with a new name and use it as the basis for your article.
\item \textbf{reference.bib}: is a plain text containing the database of the references used for the format guide. Please use the same entries included in this file for your database.
\item \textbf{bs2023.bst}: is the bibliography style of the conference proceedings. 
\end{itemize}

%---------------------------------------------------------------------------------------
\section*{Submission instruction}
%---------------------------------------------------------------------------------------

\begin{enumerate}
    \item To enable the blind review process please do not include your name and affiliation on the draft submitted for review. This information will be requested in the final submission.
    \item Please convert your entire document to PDF format. An additional doc/\LaTeX{} version of the manuscript should be added as well. If you are using \LaTeX{}, a single .zip file including all .tex, .bib and image files of your contribution shall be uploaded (must be compilable).
    \item Papers must be at most 8 pages long.
    \item You can use any file name, but please do not use special characters, umlaute, etc.
    \item The maximum file size is 10 MB, but please use vector graphics where possible to reduce your file size.
		\item If your paper has not met all the requirements for submission, your file \textbf{will not be processed for review and you will be requested to resubmit}. If everything is in order, the paper will be up-loaded to the review area of the conference website.
\end{enumerate}

%---------------------------------------------------------------------------------------
\section*{Conclusion}
%---------------------------------------------------------------------------------------

This paper has shown how to prepare a paper for submission to Building Simulation 2023 Conference. Good luck with your paper.

%---------------------------------------------------------------------------------------
\section*{Acknowledgment}
%---------------------------------------------------------------------------------------

This document is a summary of various documents from previous Building Simulation Conferences.

%here starts the references
\bibliographystyle{bs2023}
\bibliography{references}

\newpage
\onecolumn
Please \textbf{do not} include this disclaimer in your paper. You will be required to accept these conditions when you submit your paper via the website.

\begin{figure*}[ht]
\centering
\begin{boxedminipage}{\textwidth}
Building Simulation 2023\\

I or we, the author(s) and presenter(s) of the conference contribution ''Paper Preparation Guide and Submission Instructions for Building Simulation 2023 Conference'', have read the following Copyright Transfer and Disclaimer, and agree to them by submitting the final contribution materials.

  \begin{enumerate}
  \item The author(s) and presenter(s) will automatically grant to IBPSA a nonexclusive, royalty-free, perpetual, worldwide, irrevocable, sub-licensable, and transferable license to publish the abstract(s), research paper(s) and/or presentation(s) and/or digital posters (with unmodified content) in any fashion (including but not limited to inclusion in the Building Simulation 2023 printed and electronic proceedings, via electronic means such as the world wide web, and inclusion in future compilations of presentations, also including online-exploitation via electronic means in order to organize an e-conference, regardless of the accessibility through paying registration). This ''nonexclusive'' license means that the author(s) are not restricted as to future use of the material except that exclusive rights cannot be granted to another.

  \item The author(s) and presenter(s) grant and assign to IBPSA or its agent the nonexclusive rights to record the presentation at the Building Simulation 2023 conference in Shanghai, China. These rights give IBPSA the unlimited license to use, modify (format, not content), sell and distribute the recorded presentation (including voice of the presenter(s)).

  \item The author(s) and presenter(s) affirm that they have the right to grant the license specified in (1) and (2), that is, publication by IBPSA or its licensees will not be in conflict with existing copyright or other restrictions.

  \item The author(s) and presenter(s) acknowledge that acceptance of the abstract(s), research paper(s) and/or presentation(s) does not imply IBPSA's endorsement of or agreement with the ideas presented. It is understood that IBPSA does not accept responsibility for any content within the abstract(s), research paper(s) and/or presentation(s) that may be found to be libelous, infringing on copyright or other intellectual property rights, invading individual privacy or to be otherwise unlawful. Under no circumstances shall IBPSA be liable for any damages resulting from use of information included in the presentation.

  \item Finally, the undersigned confirms that he/she has the power and authority to make and execute this agreement. For jointly authored works the signing author/presenter signs as authorized agent for the others.
  \end{enumerate}

\end{boxedminipage}
\caption{The author will be required to accept these conditions when they submit their paper via the website.}
\label{fig:fig02}
\end{figure*}

\end{document}

### 2023-06-09 full-paper/paper.Rmd
paper: add full paper
paper: update

---
title: |
    Epwshiftr: incorporating open data of climate change prediction into
    \vspace{4pt}
    building performance simulation for future adaptation and mitigation
author:
  - name: Hongyuan Jia
    order: 1
    email: hongyuanjia@cqust.edu.cn
    affiliation: |
        Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
  - name: Baisong Ning
    order: 2
    email: bsning@foxmail.com
    affiliation: |
        Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China

abstract: |
  Future weather data is a prerequisite for accessing the impacts of climate
  change on building energy performance. The Morphing statistical downscaling
  method, which utilizes the Global Climate Model (GCM) output, is a relatively
  simple and reliable method for future weather data prediction and is widely
  used in current research/tools. However, existing weather generators typically
  assume a single GCM or can only consider GCMs from the old CMIP (Coupled Model
  Intercomparison Project) projects published more than ten years ago. This
  paper presents a free, open-source tool called epwshiftr for incorporating
  open data from the latest CMIP6 project into EnergyPlus Weather (EPW)
  generation using the Morphing method. The focus of this tool is to ease the
  burden of the cumbersome data preparation process as much as possible while
  providing user-friendly and flexible ways to create future EPWs for worldwide
  locations.

bibliography: references.bib

output:
  bookdown::pdf_document2:
    template: template/bs2023.tex
    citation_package: natbib
    keep_tex: true

date: "2023-05-27"
id: 1612

blind: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  eval = FALSE,
  comment = "#>",
  out.width = "\\columnwidth"
)
```

# Highlights

- A free open-source future weather generator `epwshiftr` was developed.
- It utilizes the latest CMIP6 ScenarioMIP experiment data
- It can automatically process significant amounts of climate change model data
  worldwide.
- It can generate future weather data for 11 meteorological variables.

# Introduction

Building energy simulation (BES) has become increasingly applied to assess
building performance under climate change and yield a more sustainable and
resilient design [@yassaghi2019overview]. Weather files form the boundary
conditions of BES and directly affect the results [@bhandari2012evaluation].
Therefore, it is necessary to use further weather data considering climate
change for the design and performance evaluation of new and existing buildings
[@picard2020robustness].

A rich body of research and development exists on weather generators for
creating future weather data for BES. In 2005, @belcher2005constructing proposed
the morphing method, a relatively simple and reliable statistical downscaling
method. It is based on the future climate change data predicted by the Global
Climate Model (GCM) and hourly weather data, usually a typical meteorological
year (TMY). Morphing can capture the average future weather conditions from GCM
while preserving historical weather sequences. Multiple future weather
generators have been developed over the decades to integrate climate change
predictions from CMIP (Coupled Model Intercomparison Project) projects that
cover worldwide locations [@jentsch2008climate; @troup2016morphing;
@dickinson2016generating; @yassaghi2019overview]. Currently,
CCWorldWeatherGen[@jentsch2013transforming], WeatherShift
[@dickinson2016generating], and Meteonorm [@remund2020meteonorm] are three
future weather generators widely used in literature. CCWorldWeatherGen provides
a graphical interface based on Microsoft Excel to generate weather files in EPW
format supported by EnergyPlus directly. However, it is based on the A2 climate
scenario from the IPCC Third Assessment Report (TAR) published in 2001. Moreover,
it only utilizes data from a single GCM called HadCM3. Like CCWorldWeatherGen,
WeatherShift and Meteonorm also use morphing to generate EPW files for future
climate. They consider two representative concentration pathway (RCP) emission
scenarios, i.e. RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
Assessment Report (AR5). At the same time, both are commercial products, and the
weather data under a single climate scenario often cost hundreds of dollars.

Currently, the CMIP project is in its sixth phase (CMIP6), which has developed
new emission scenarios that have a similar range as the CMIP5, but fill critical
gaps for intermediate forcing levels [@oneill2016scenario]. IPCC
(Intergovernmental Panel on Climate Change) released the sixth climate
assessment report (AR6) based on CMIP6. It is based on the latest Shared
Socio-economic Pathway (SSP) climate change projections proposed by the CMIP6
ScenarioMIP experiment results.

Compared with the representative concentration pathway (RCP) scenarios in IPCC
AR5, the new scenarios based on SSP consider the impact of changes in
socio-economic factors on climate change, such as population, economic growth,
education, urbanization, etc [@chakraborty2021scenariobased]. Therefore,
existing research using outdated IPCC emission scenarios may not reasonably and
effectively represent the climate impacts and socio-economic risks of different
policy options.

Moreover, there are no easy-access tools for predicting future meteorological
parameters based on the latest SSP emission scenarios.

To this end, this paper proposes a future weather generation method for BES
based on CMIP6 ScenarioMIP climate scenarios, and develops a a free and
open-source tool epwshiftr. It incorporates open data from the latest CMIP6
project into EnergyPlus Weather (EPW) generation using the morphing method. The
focus of this tool is to ease the burden of the cumbersome data preparation
process as much as possible while providing user-friendly and flexible ways to
create future EPWs for worldwide locations. It takes full advantage of data
query and fetching interfaces provided by the Earth System Grid Federation (ESGF)
portals where CMIP6 data are held. Epwshiftr can process multiple GCM outputs at
various spatial and temporal resolutions. Each module of epwshiftr stores data
in a standard data format, providing possibilities for exploring a considerably
broad pool of ready-to-use methods available for customized statistical
analysis. Most computational-intensive processes have been designed to run in
parallel for speed-up.

# Climate scenarios in CMIP6 ScenarioMIP

CMIP6 provides climate change simulation and forecast data and forms the
scientific basis of the IPCC assessment report. It approved 23 Model Comparison
Sub-Projects (MIPs). ScenarioMIP, one of those MIPs, aims to provide critical
data support for future climate change mechanism studies and corresponding
mitigation and adaptation research. The new climate projection scenarios
proposed by ScenarioMIP are rectangular combinations of different Shared
Socio-economic Pathways (SSPs) and the latest Representative Concentration
Pathways (RCPs):

1. SSP is used to describe the possible development scenarios of the future
   society without the influence of climate change or climate policy (CMIP6,
   2014). There are five SSP scenarios in ScenarioMIP, namely SSP1, SSP2, SSP3,
   SSP4, and SSP5, arranged in order of social development from good to bad,
   representing sustainable, moderate, partial, unbalanced, and normal
   development, respectively.

2. RCP represents the level of global radiative forcing, i.e., the amount of
   change in the net irradiance of the tropopause or the top of the atmosphere
   due to climate change until the end of this century. Based on the four
   radiative forcing levels in the CMIP5 RCP, ScenarioMIP added three new
   emission pathways, namely RCP2.6, RCP3.4, and RCP7.0, filling the gaps
   between the typical pathways of CMIP6 [@oneill2016scenario].

ScenarioMIP combines the above five SSP scenarios and seven RCPs to form eight
groups of future climate scenarios. They are grouped into Tier-1 and Tier-2
based on the modeling priority, with Tier-1 being the core test, as shown in
Figure \@ref(fig:ssp).

```{r}
#| ssp,
#| echo = FALSE,
#| eval = TRUE,
#| fig.cap = "Scenario design matrix for future climate prediction based on SSP
#|   and RCP in ScenarioMIP\\citep{oneill2016scenario}"

knitr::include_graphics("figures/ssp.png")
```

# `epwshiftr`: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data

Epwshiftr is developed using R [@RCoreTeam2019] language and distributed
using CRAN (Comprehensive R Archive Network)^[epwshiftr CRAN link:
https://cran.r-project.org/package=epwshiftr]. It can be downloaded for free
and run on common platforms, including Windows, macOS, and Linux. Epwshiftr is
open-source, and the source code is published on GitHub^[epwshiftr GitHub link:
https://github.com/ideas-lab-nus/epwshiftr]. Epwshiftr can be easily installed
via a single command as shown in Listing \ref{lst:install}.

\begin{listing}
\caption{Install epwshiftr}\label{lst:install}
\includegraphics[width=\columnwidth]{figures/code-install.png}
\end{listing}

Figure \@ref(fig:workflow) shows the primary process of using epwshiftr to
generate EPW files for future weather. It consists of five modules, including:

- ***Query Module***, which sends queries of the CMIP6 ScenarioMIP output using
  the Earth System Grid Federation (ESGF) portals;
- ***Database Module***, which is used to manage the massive raw climate change data
  of ScenarioMIP GCMs;
- ***Data Extraction Module***, which can extract climate change raw data based on
  geographic location information;
- ***Morphing Module***, which uses the morphing statistical downscaling method to
  calculate the predicted values of each meteorological variable at different
  future time periods and under different climate forecast scenarios;
- ***EPW Generation Module***, which uses the forecast data to generate EPW files
  under future climate change, based on the mapping between EPW weather
  variables and GCM output meteorological variables.

```{r}
#| workflow,
#| echo = FALSE,
#| eval = TRUE,
#| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"

knitr::include_graphics("figures/workflow.png")
```

With the generated future meteorological data, future building loads and energy
demand under climate change can be predicted and evaluated. Many tools are
currently available to perform parametric BES. Eplusr [@jia2021eplusr], a rich
toolset for BES data-driven analyses, is one of them and can be integrated well
with epwshiftr. Evaluation of future building energy demand using generated
future weather data is not the focus of this paper. The following sections will
explain the implementation principle and technical details of epwshiftr by
module.

## Query ScenarioMIP GCM output using ESGF

CMIP6 is still an ongoing program in which global climatologists share, analyze,
and compare simulation results from the latest GCMs. All GCM outputs in CMIP6
are available for free download through the Earth System Grid Federation (ESGF).
ESGF provides GCM outputs in NetCDF format, a widely-used format in the earth
science domain. It divides the data based on climate variables, output
frequencies, GCMs, variant labels, earth grid types, time ranges, and other
dimensions.

Since each NetCDF file contains data of a complete global grid, the size of the
monthly global surface temperature forecast data for the next 20 years under a
single climate scenario can reach more than 1 GB. The CMIP6 ScenarioMIP contains
dozens of different GCMs, and the total size of all output files will get more
than 10 TB, making it impossible to download all of them for analysis.

The *Query Module* provides an interface utilizing the RESTful API provided by
ESGF and thus is capable of querying all CMIP6 GCM outputs based on various
conditions, providing download links of NetCDF files. The query result will be
processed into a data frame that contains 22 metadata that describes each
output. Also, an output index is generated based on the query and is used to
check the data integrity before extracting climate change data.

Listing 2 demonstrates how to use the `index_cmip6_index` interface from the
*Query Module*.

This snippet will send a query to ESGF to list all available daily outputs for
near-surface air temperature (tas) and relative humidity (hurs) from
AWI-CM-1-1-MR GCM first run (r1i1p1f1) under SSP585 climate scenario from the
ScenarioMIP activity for year 2050 and 2080. Also an output index file named
"cmip6_index.csv" will be saved.

\begin{listing}
\caption{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
\includegraphics[width=\columnwidth]{figures/code-index.png}
\end{listing}

## GCM raw output data management

As mentioned above, the size of NetCDF files can easily reach hundreds of GB or
even TB levels for multiple combinations of emission scenarios and GCMs, as
shown in Figure \@ref(fig:db). Therefore, it becomes cumbersome to manage such
massive data properly.

```{r}
#| db,
#| echo = FALSE,
#| eval = TRUE,
#| fig.cap = "GCM outputs in NetCDF files for 11 variables from 10 GCMs under 4
#|   climate scenarios from 2020 to 2100 take 2.81TB space with more than 13,000
#|   files"

knitr::include_graphics("figures/db.png")
```

Fortunately, CMIP6 requires each NetCDF file generated by GCM to contain
specific global attributes, which can be used to describe the data stored in the
file. Among them, 30 are mandatory and are included in every file. Therefore,
the *Database Module* creates a mapping between the ESGF query output and each
global attribute and manages the original big data of ScenarioMIP GCM climate
change. Since the amount of data to extract from the global attributes in NetCDF
is negligible compared to the total data volume of the time-series matrix, the
computational load is small. It should be pointed out that CMIP6 does not
require a specific calendar format for the time series GCM output. Various
calendars exist, including the standard calendar, proleptic gregorian calendar,
365-day calendar, 366-day calendar, 360-day calendar, etc. Therefore, careful
attention has been paid when converting the time range information obtained from
ESGF and NetCDF files to ensure they are all transformed to the standard
calendar.

To speed up the data verification process, the *Database Module* uses
asynchronous parallel computing to extract and verify attributes of multiple
NetCDF files simultaneously. This parallel computing is also applied to all
other modules that perform computational-intensive procedures.

Listing \ref{lst:db} demonstrates how to use the `suumary_database` interface from the
Database Module to get a summary of NetCDF files downloaded against the CMIP6
output index generated using the *Query Module.* This step is necessary as it maps
the loaded files against index so that epwshiftr knows which case is complete
and can be used for the next step.

\begin{listing}
\caption{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
\includegraphics[width=\columnwidth]{figures/code-db.png}
\end{listing}

## Extraction of raw climate change data based on geographic location

When the integrity check has been passed, the next step is to extract the raw
time-series data from GCM NetCDF output files. NetCDF stores data as a
three-dimensional time, longitude, and latitude matrix. Therefore, the data can
be extracted through the target location's geographic location information
(latitude and longitude). However, the global grid from GCMs is often coarse.
The spatial resolution is generally around 50km to 100 km, making obtaining
accurate data of target locations challenging. In addition, the spacing of
longitude and latitude in the global grid is usually different. Currently, no
uniform standard method exists to calculate the distance between two points on a
global grid. The common methods are: (a) Euler distance method, (b) Tunnel
Distance method and (c) K-D tree algorithm. The Data Extraction Module uses the
Euler distance method. Moreover, it also provides parameters to specify the
distance threshold of longitude and latitude on the grid from the target
position and the maximum number of grid points to match. Similarly, all data
extraction processes are implemented in parallel to speed up.

\begin{listing}
\caption{Match the global grid points directly using an EPW file and extract raw GCM data}\label{lst:data}
\includegraphics[width=\columnwidth]{figures/code-data.png}
\end{listing}

Listing \ref{lst:data} demonstrates how to use the `match_coord` interface from
the *Data Extract Module* to extract all coordinates and data of grid points that
meet the specified requirements, i.e., the maximum geographical distance between
the matched grid points and selected location should be less than 0.5 degree,
and only return the closest point. It also showcases the ability of directly
using an EPW file as input for coordinate matching, as epwshiftr can parse the
geographical information stored in EPW files.

The extracted raw data will be distinguished by six attributes: MIP, GCM,
climate scenario, output frequency, geographic location (longitude and latitude),
and climate variables. This makes the post-processing and analysis of raw
climate change data can be easily realized.

The size of the raw data extracted can be relatively big. For example, based on
the authors' measurements, it takes about 20G memory to read the raw data of 12
climate variables from 2020 to 2100 from 4 climate scenarios and 11 GCMs, which
is often close to, if not greater than, a normal PC's memory. For this reason,
epwshiftr supports storing the original data in the fst format [@mark2022fst]
with a super large compression ratio, which greatly reduces the content burden
required for calculation. Still taking the above situation as an example, if the
data is divided by GCM, the size of a single fst file is only about 50MB, which
can be easily read and processed by current mainstream home computers.

## Generation of future weather data using morphing statistical downscaling

The *Morphing Module* is closely related to the EPW Generation Module and will
be described together in this section. After obtaining the raw GCM climate
prediction data, the last step is to generate EPW weather files that can be
directly used for energy simulation programs like EnergyPlus through the
Morphing statistical downscaling method. Compared with the time-consuming raw
data preparation process described above, generating climate files using
morphing statistical downscaling is relatively simple. The morphing method
involves calculating the future hourly weather parameter $x$ by applying a
stretching factor and/or a shifting factor to the original weather value $x_0$
(see Equation \ref{eq:morph-shift}-\ref{eq:morph-mixed}). It captures the
average climate change while preserving the physically realistic source weather
data sequences.

\begin{align}
\text{Shift:}         \: & x = x_0 + \Delta x_m \label{eq:morph-shift}\\
\text{Stretch:}       \: & x = \alpha _m x_m    \label{eq:morph-stretch}\\
\text{Shift+Stretch:} \: & x = x_0 + \Delta x_m + a_m ( x_0 - \langle x_0 \rangle _m ) \label{eq:morph-mixed}
\end{align}

where $x_0$ is the weather data for the current hour; $\Delta x_m$ is the mean
monthly change in the weather data x obtained from the GCMs; $\alpha _m$ is the
stretching factor; and $\langle x_0 \rangle$ is the monthly mean of the current
weather data.

Epwshiftr can generate future data for the following 11 weather variables:

* Dry-bulb temperature
* Dew-point temperature
* Relative humidity
* Atmospheric pressure
* Horizontal infrared radiation
* Total horizontal radiation
* Direct normal radiation
* Diffuse horizontal radiation
* Outdoor wind speed
* Total sky cover
* Opaque sky cover

At the same time, when generating EPW files, average processing can also be
performed based on GCM, output frequency, longitude, latitude, etc.

Listing \ref{lst:epw} demonstrates how to use the `morphing_epw` interface from
the *Morphing Module* and the `future_epw` interface from the *EPW Generation
Module* to perform morphing on the baseline EPW data and raw GCM data, and
create future EPW files based on the GCM source, climate scenarios and time
interval. All EPW files will be saved into a seprate folder.

\begin{listing}
\caption{Perform morphing and generate future EPWs}\label{lst:epw}
\includegraphics[width=\columnwidth]{figures/code-epw.png}
\end{listing}

# Conclusion

This paper presents a free, open-source R package called epwshiftr for adapting
EnergyPlus Weather (EPW) files to incorporate climate change predictions using
the morphing method. It can utilize the latest CMIP6 ScenarioMIP experiment data
and automatically process significant amounts of climate change model data
worldwide. This tool will significantly save the time and cost of obtaining
future weather data and thus can support the analysis of future building heating
and air-conditioning demand, energy consumption, and carbon emissions.

# References {-}

### 2023-06-09 full-paper/paper.tex
paper: add full paper
paper: update

--- 2023-06-09 full-paper/paper.Rmd
@@
----
-title: |
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Template revision history:
+% BS2023: Revised by Yikun Yang, ian@tongji.edu.cn
+% BS2021: Revised by Filip Jorissen, filip.jorissen@kuleuven.be
+% BS2019: Revised by Alessandro Prada, alessandro.prada@unitn.it
+% BS2017: Initial version by Michael Wetter, mwetter@lbl.gov
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[twocolumn, a4paper,10pt]{article}
+\usepackage[top=2.5cm, bottom=2.5cm, left=2.0cm, right=2.0cm,
+columnsep=0.8cm]{geometry}
+\usepackage{enumitem}
+\usepackage[hidelinks]{hyperref}
+\usepackage{boxedminipage}
+\usepackage{nopageno}
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage[font=it]{caption}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{listings}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{newfloat}
+%-----------------------------SET SKIP SPACES -------------------------------------------------------------------
+\setlength{\abovecaptionskip}{0pt}
+\setlength{\belowcaptionskip}{3pt}
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{3pt}
+%\renewcommand{\baselinestretch}{0.7}
+% FOR enumerates
+\setlist{itemsep=-0.1cm,topsep=0.1cm,labelsep=0.3cm}
+\setenumerate{leftmargin=*}
+\setcounter{secnumdepth}{-1}
+%-----------------------------CODE FORMATTING -------------------------------------------------------------------
+\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setlist[itemize]{leftmargin=*}
+% cross-reference code chunks
+% Reference: https://stackoverflow.com/questions/50702942/does-rmarkdown-allow-captions-and-references-for-code-chunks
+\usepackage{floatrow}
+\usepackage{color}
+\usepackage{fancyvrb}
+\usepackage{mdframed}
+
+\definecolor{shadecolor}{RGB}{248,248,248}
+
+\floatsetup[table]{capposition=top}
+
+% add caption for codes
+\DeclareNewFloatType{Code}{placement=h, fileext=code, name=Listing}
+\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}
+\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}
+
+% add a custom float environment for listing in figure format
+\DeclareFloatingEnvironment[
+    fileext=los,
+    listname={List of Listings},
+    name=Listing,
+    placement=tbhp
+]{listing}
+
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{%
+    commandchars=\\\{\},
+    fontsize=\scriptsize,
+    numbers=left,
+    numbersep=5pt
+}
+\newenvironment{Shaded}{\captionof{Code}{} \begin{mdframed}[skipabove=0pt]}{\end{mdframed}}
+\mdfsetup{%
+    innerleftmargin=3pt,
+    innerrightmargin=3pt,
+    innertopmargin=3pt,
+    innerbottommargin=3pt,
+    backgroundcolor=shadecolor
+}
+% adopted from pandoc
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+%-----------------------------SET FONTS -------------------------------------------------------------------
+% Set fonts for title, section and subsection headings
+\makeatletter
+\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
+\makeatletter
+\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
+% \normalfont\large
+\makeatletter
+\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
+\makeatletter
+\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
+\renewcommand\refname{References}
+%END OF THE SETUP
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Please keep the \vspace{4pt} at the top
+\title{%
 Epwshiftr: incorporating open data of climate change prediction into
 \vspace{4pt}
-    building performance simulation for future adaptation and mitigation
-author:
-  - name: Hongyuan Jia
-    order: 1
-    email: hongyuanjia@cqust.edu.cn
-    affiliation: |
-        Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
-  - name: Baisong Ning
-    order: 2
-    email: bsning@foxmail.com
-    affiliation: |
-        Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China
+building performance simulation for future adaptation and mitigation\\																								% Line 1
+%%% Please keep the \vspace{4pt} between lines in the title
+} 																																% Line 2
+%If there is no second line then just put \phantom{Line 2} here
+%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
+%%% Do not exceed more than 6 lines for authors and affiliations
+\author{																																														% Line 3
+    \phantom{Line 4}\\
+  \phantom{Line 5}\\
+  \phantom{Line 6}\\
+  \phantom{Line 7}\\
+  \phantom{Line 8}\\
+  \phantom{Line 9}
+  } 																																									% Line 9
+\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
+%END OF THE TITLE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
 
-abstract: |
+\maketitle
+
+\section*{Abstract}	% Section headings need to be upper and lower case.
+\addtocounter{section}{1}
 Future weather data is a prerequisite for accessing the impacts of climate
@@
 
-bibliography: references.bib
+\hypertarget{highlights}{%
+\section{Highlights}\label{highlights}}
 
-output:
-  bookdown::pdf_document2:
-    template: template/bs2023.tex
-    citation_package: natbib
-    keep_tex: true
+\begin{itemize}
+\tightlist
+\item
+  A free open-source future weather generator \texttt{epwshiftr} was developed.
+\item
+  It utilizes the latest CMIP6 ScenarioMIP experiment data
+\item
+  It can automatically process significant amounts of climate change model data
+  worldwide.
+\item
+  It can generate future weather data for 11 meteorological variables.
+\end{itemize}
 
-date: "2023-05-27"
-id: 1612
-
-blind: true
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = TRUE,
-  eval = FALSE,
-  comment = "#>",
-  out.width = "\\columnwidth"
-)
-```
-
-# Highlights
-
-- A free open-source future weather generator `epwshiftr` was developed.
-- It utilizes the latest CMIP6 ScenarioMIP experiment data
-- It can automatically process significant amounts of climate change model data
-  worldwide.
-- It can generate future weather data for 11 meteorological variables.
-
-# Introduction
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 building performance under climate change and yield a more sustainable and
-resilient design [@yassaghi2019overview]. Weather files form the boundary
-conditions of BES and directly affect the results [@bhandari2012evaluation].
+resilient design \citep{yassaghi2019overview}. Weather files form the boundary
+conditions of BES and directly affect the results \citep{bhandari2012evaluation}.
 Therefore, it is necessary to use further weather data considering climate
 change for the design and performance evaluation of new and existing buildings
-[@picard2020robustness].
+\citep{picard2020robustness}.
 
 A rich body of research and development exists on weather generators for
-creating future weather data for BES. In 2005, @belcher2005constructing proposed
+creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
 the morphing method, a relatively simple and reliable statistical downscaling
@@
 predictions from CMIP (Coupled Model Intercomparison Project) projects that
-cover worldwide locations [@jentsch2008climate; @troup2016morphing;
-@dickinson2016generating; @yassaghi2019overview]. Currently,
-CCWorldWeatherGen[@jentsch2013transforming], WeatherShift
-[@dickinson2016generating], and Meteonorm [@remund2020meteonorm] are three
+cover worldwide locations \citep{jentsch2008climate, troup2016morphing, dickinson2016generating, yassaghi2019overview}. Currently,
+CCWorldWeatherGen\citep{jentsch2013transforming}, WeatherShift
+\citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
 future weather generators widely used in literature. CCWorldWeatherGen provides
@@
 climate. They consider two representative concentration pathway (RCP) emission
-scenarios, i.e. RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
+scenarios, i.e.~RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
 Assessment Report (AR5). At the same time, both are commercial products, and the
@@
 new emission scenarios that have a similar range as the CMIP5, but fill critical
-gaps for intermediate forcing levels [@oneill2016scenario]. IPCC
+gaps for intermediate forcing levels \citep{oneill2016scenario}. IPCC
 (Intergovernmental Panel on Climate Change) released the sixth climate
@@
 socio-economic factors on climate change, such as population, economic growth,
-education, urbanization, etc [@chakraborty2021scenariobased]. Therefore,
+education, urbanization, etc \citep{chakraborty2021scenariobased}. Therefore,
 existing research using outdated IPCC emission scenarios may not reasonably and
@@
 
-# Climate scenarios in CMIP6 ScenarioMIP
+\hypertarget{climate-scenarios-in-cmip6-scenariomip}{%
+\section{Climate scenarios in CMIP6 ScenarioMIP}\label{climate-scenarios-in-cmip6-scenariomip}}
 
@@
 
-1. SSP is used to describe the possible development scenarios of the future
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  SSP is used to describe the possible development scenarios of the future
   society without the influence of climate change or climate policy (CMIP6,
@@
   development, respectively.
-
-2. RCP represents the level of global radiative forcing, i.e., the amount of
+\item
+  RCP represents the level of global radiative forcing, i.e., the amount of
   change in the net irradiance of the tropopause or the top of the atmosphere
@@
   emission pathways, namely RCP2.6, RCP3.4, and RCP7.0, filling the gaps
-   between the typical pathways of CMIP6 [@oneill2016scenario].
+  between the typical pathways of CMIP6 \citep{oneill2016scenario}.
+\end{enumerate}
 
@@
 based on the modeling priority, with Tier-1 being the core test, as shown in
-Figure \@ref(fig:ssp).
+Figure \ref{fig:ssp}.
 
-```{r}
-#| ssp,
-#| echo = FALSE,
-#| eval = TRUE,
-#| fig.cap = "Scenario design matrix for future climate prediction based on SSP
-#|   and RCP in ScenarioMIP\\citep{oneill2016scenario}"
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/ssp} \caption{Scenario design matrix for future climate prediction based on SSP  and RCP in ScenarioMIP\citep{oneill2016scenario}}\label{fig:ssp}
+\end{figure}
 
-knitr::include_graphics("figures/ssp.png")
-```
+\hypertarget{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}{%
+\section{\texorpdfstring{\texttt{epwshiftr}: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}{epwshiftr: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}}\label{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}}
 
-# `epwshiftr`: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data
-
-Epwshiftr is developed using R [@RCoreTeam2019] language and distributed
-using CRAN (Comprehensive R Archive Network)^[epwshiftr CRAN link:
-https://cran.r-project.org/package=epwshiftr]. It can be downloaded for free
+Epwshiftr is developed using R \citep{RCoreTeam2019} language and distributed
+using CRAN (Comprehensive R Archive Network)\footnote{epwshiftr CRAN link:
+  \url{https://cran.r-project.org/package=epwshiftr}}. It can be downloaded for free
 and run on common platforms, including Windows, macOS, and Linux. Epwshiftr is
-open-source, and the source code is published on GitHub^[epwshiftr GitHub link:
-https://github.com/ideas-lab-nus/epwshiftr]. Epwshiftr can be easily installed
+open-source, and the source code is published on GitHub\footnote{epwshiftr GitHub link:
+  \url{https://github.com/ideas-lab-nus/epwshiftr}}. Epwshiftr can be easily installed
 via a single command as shown in Listing \ref{lst:install}.
@@
 
-Figure \@ref(fig:workflow) shows the primary process of using epwshiftr to
+Figure \ref{fig:workflow} shows the primary process of using epwshiftr to
 generate EPW files for future weather. It consists of five modules, including:
 
-- ***Query Module***, which sends queries of the CMIP6 ScenarioMIP output using
+\begin{itemize}
+\tightlist
+\item
+  \textbf{\emph{Query Module}}, which sends queries of the CMIP6 ScenarioMIP output using
   the Earth System Grid Federation (ESGF) portals;
-- ***Database Module***, which is used to manage the massive raw climate change data
+\item
+  \textbf{\emph{Database Module}}, which is used to manage the massive raw climate change data
   of ScenarioMIP GCMs;
-- ***Data Extraction Module***, which can extract climate change raw data based on
+\item
+  \textbf{\emph{Data Extraction Module}}, which can extract climate change raw data based on
   geographic location information;
-- ***Morphing Module***, which uses the morphing statistical downscaling method to
+\item
+  \textbf{\emph{Morphing Module}}, which uses the morphing statistical downscaling method to
   calculate the predicted values of each meteorological variable at different
   future time periods and under different climate forecast scenarios;
-- ***EPW Generation Module***, which uses the forecast data to generate EPW files
+\item
+  \textbf{\emph{EPW Generation Module}}, which uses the forecast data to generate EPW files
   under future climate change, based on the mapping between EPW weather
   variables and GCM output meteorological variables.
+\end{itemize}
 
-```{r}
-#| workflow,
-#| echo = FALSE,
-#| eval = TRUE,
-#| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"
-
-knitr::include_graphics("figures/workflow.png")
-```
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/workflow} \caption{The primary process of using epwshiftr to generate EPW files for future weather}\label{fig:workflow}
+\end{figure}
 
@@
 demand under climate change can be predicted and evaluated. Many tools are
-currently available to perform parametric BES. Eplusr [@jia2021eplusr], a rich
+currently available to perform parametric BES. Eplusr \citep{jia2021eplusr}, a rich
 toolset for BES data-driven analyses, is one of them and can be integrated well
@@
 
-## Query ScenarioMIP GCM output using ESGF
+\hypertarget{query-scenariomip-gcm-output-using-esgf}{%
+\subsection{Query ScenarioMIP GCM output using ESGF}\label{query-scenariomip-gcm-output-using-esgf}}
 
@@
 
-The *Query Module* provides an interface utilizing the RESTful API provided by
+The \emph{Query Module} provides an interface utilizing the RESTful API provided by
 ESGF and thus is capable of querying all CMIP6 GCM outputs based on various
@@
 
-Listing 2 demonstrates how to use the `index_cmip6_index` interface from the
-*Query Module*.
+Listing 2 demonstrates how to use the \texttt{index\_cmip6\_index} interface from the
+\emph{Query Module}.
 
@@
 ScenarioMIP activity for year 2050 and 2080. Also an output index file named
-"cmip6_index.csv" will be saved.
+``cmip6\_index.csv'' will be saved.
 
@@
 
-## GCM raw output data management
+\hypertarget{gcm-raw-output-data-management}{%
+\subsection{GCM raw output data management}\label{gcm-raw-output-data-management}}
 
@@
 even TB levels for multiple combinations of emission scenarios and GCMs, as
-shown in Figure \@ref(fig:db). Therefore, it becomes cumbersome to manage such
+shown in Figure \ref{fig:db}. Therefore, it becomes cumbersome to manage such
 massive data properly.
 
-```{r}
-#| db,
-#| echo = FALSE,
-#| eval = TRUE,
-#| fig.cap = "GCM outputs in NetCDF files for 11 variables from 10 GCMs under 4
-#|   climate scenarios from 2020 to 2100 take 2.81TB space with more than 13,000
-#|   files"
-
-knitr::include_graphics("figures/db.png")
-```
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/db} \caption{GCM outputs in NetCDF files for 11 variables from 10 GCMs under 4  climate scenarios from 2020 to 2100 take 2.81TB space with more than 13,000  files}\label{fig:db}
+\end{figure}
 
@@
 file. Among them, 30 are mandatory and are included in every file. Therefore,
-the *Database Module* creates a mapping between the ESGF query output and each
+the \emph{Database Module} creates a mapping between the ESGF query output and each
 global attribute and manages the original big data of ScenarioMIP GCM climate
@@
 
-To speed up the data verification process, the *Database Module* uses
+To speed up the data verification process, the \emph{Database Module} uses
 asynchronous parallel computing to extract and verify attributes of multiple
@@
 
-Listing \ref{lst:db} demonstrates how to use the `suumary_database` interface from the
+Listing \ref{lst:db} demonstrates how to use the \texttt{suumary\_database} interface from the
 Database Module to get a summary of NetCDF files downloaded against the CMIP6
-output index generated using the *Query Module.* This step is necessary as it maps
+output index generated using the \emph{Query Module.} This step is necessary as it maps
 the loaded files against index so that epwshiftr knows which case is complete
@@
 
-## Extraction of raw climate change data based on geographic location
+\hypertarget{extraction-of-raw-climate-change-data-based-on-geographic-location}{%
+\subsection{Extraction of raw climate change data based on geographic location}\label{extraction-of-raw-climate-change-data-based-on-geographic-location}}
 
@@
 
-Listing \ref{lst:data} demonstrates how to use the `match_coord` interface from
-the *Data Extract Module* to extract all coordinates and data of grid points that
+Listing \ref{lst:data} demonstrates how to use the \texttt{match\_coord} interface from
+the \emph{Data Extract Module} to extract all coordinates and data of grid points that
 meet the specified requirements, i.e., the maximum geographical distance between
@@
 is often close to, if not greater than, a normal PC's memory. For this reason,
-epwshiftr supports storing the original data in the fst format [@mark2022fst]
+epwshiftr supports storing the original data in the fst format \citep{mark2022fst}
 with a super large compression ratio, which greatly reduces the content burden
@@
 
-## Generation of future weather data using morphing statistical downscaling
+\hypertarget{generation-of-future-weather-data-using-morphing-statistical-downscaling}{%
+\subsection{Generation of future weather data using morphing statistical downscaling}\label{generation-of-future-weather-data-using-morphing-statistical-downscaling}}
 
-The *Morphing Module* is closely related to the EPW Generation Module and will
+The \emph{Morphing Module} is closely related to the EPW Generation Module and will
 be described together in this section. After obtaining the raw GCM climate
@@
 morphing statistical downscaling is relatively simple. The morphing method
-involves calculating the future hourly weather parameter $x$ by applying a
-stretching factor and/or a shifting factor to the original weather value $x_0$
+involves calculating the future hourly weather parameter \(x\) by applying a
+stretching factor and/or a shifting factor to the original weather value \(x_0\)
 (see Equation \ref{eq:morph-shift}-\ref{eq:morph-mixed}). It captures the
@@
 
-where $x_0$ is the weather data for the current hour; $\Delta x_m$ is the mean
-monthly change in the weather data x obtained from the GCMs; $\alpha _m$ is the
-stretching factor; and $\langle x_0 \rangle$ is the monthly mean of the current
+where \(x_0\) is the weather data for the current hour; \(\Delta x_m\) is the mean
+monthly change in the weather data x obtained from the GCMs; \(\alpha _m\) is the
+stretching factor; and \(\langle x_0 \rangle\) is the monthly mean of the current
 weather data.
@@
 
-* Dry-bulb temperature
-* Dew-point temperature
-* Relative humidity
-* Atmospheric pressure
-* Horizontal infrared radiation
-* Total horizontal radiation
-* Direct normal radiation
-* Diffuse horizontal radiation
-* Outdoor wind speed
-* Total sky cover
-* Opaque sky cover
+\begin{itemize}
+\tightlist
+\item
+  Dry-bulb temperature
+\item
+  Dew-point temperature
+\item
+  Relative humidity
+\item
+  Atmospheric pressure
+\item
+  Horizontal infrared radiation
+\item
+  Total horizontal radiation
+\item
+  Direct normal radiation
+\item
+  Diffuse horizontal radiation
+\item
+  Outdoor wind speed
+\item
+  Total sky cover
+\item
+  Opaque sky cover
+\end{itemize}
 
@@
 
-Listing \ref{lst:epw} demonstrates how to use the `morphing_epw` interface from
-the *Morphing Module* and the `future_epw` interface from the *EPW Generation
-Module* to perform morphing on the baseline EPW data and raw GCM data, and
+Listing \ref{lst:epw} demonstrates how to use the \texttt{morphing\_epw} interface from
+the \emph{Morphing Module} and the \texttt{future\_epw} interface from the \emph{EPW Generation
+Module} to perform morphing on the baseline EPW data and raw GCM data, and
 create future EPW files based on the GCM source, climate scenarios and time
@@
 
-# Conclusion
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 
-# References {-}
+%here starts the references
+\bibliography{references.bib}
+\bibliographystyle{template/bs2023}
+
+\end{document}

### 2023-06-09 full-paper/paper.Rmd
paper: fix typos

@@
 conditions of BES and directly affect the results [@bhandari2012evaluation].
-Therefore, it is necessary to use further weather data considering climate
+Therefore, it is necessary to use future weather data considering climate
 change for the design and performance evaluation of new and existing buildings

### 2023-06-09 full-paper/paper.Rmd
paper: use hi-res figures and set width as text width

@@
 #| eval = TRUE,
+#| out.width = "0.7\\textwidth",
+#| fig.env = "figure*",
 #| fig.cap = "Scenario design matrix for future climate prediction based on SSP
@@
 
-knitr::include_graphics("figures/ssp.png")
+knitr::include_graphics("figures/ssp-hires.png")
 ```
@@
 #| eval = TRUE,
+#| out.width = "0.7\\textwidth",
+#| fig.env = "figure*",
 #| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"
 
-knitr::include_graphics("figures/workflow.png")
+knitr::include_graphics("figures/workflow-hires.png")
 ```

### 2023-06-09 full-paper/paper.Rmd
paper: address reviewer comments

--- 2023-06-09 full-paper/paper.Rmd
@@
   method, which utilizes the Global Climate Model (GCM) output, is a relatively
-  simple and reliable method for future weather data prediction and is widely
+  simple method for future weather data prediction and is widely
   used in current research/tools. However, existing weather generators typically
@@
 )
+
+hooks <- knitr::knit_hooks$get("source")
+knitr::knit_hooks$set(source = function(x, options) {
+  x <- hooks(x, options)
+  x <- ifelse(!is.null(options$code.ref), paste0("\\label{", options$code.ref, "}", x), x)
+  ifelse(!is.null(options$code.cap), paste0("\\captionof{code}{", options$code.cap, "}", x), x)
+})
 ```
@@
 creating future weather data for BES. In 2005, @belcher2005constructing proposed
-the morphing method, a relatively simple and reliable statistical downscaling
+the morphing method, a relatively simple statistical downscaling
 method. It is based on the future climate change data predicted by the Global
@@
 year (TMY). Morphing can capture the average future weather conditions from GCM
-while preserving historical weather sequences. Multiple future weather
+while preserving historical weather sequences. It requires low computational
+power, making it possible to create many weather files from worldwide locations.
+However, morphing may under- or overestimate climate change impacts because of
+the lacking of ability to capture future extreme weather conditions and
+potential differences in the reference time frame of the TMY and GCM data
+[@moazami2019impacts].
+Moreover, careful consideration should be given to morphing when modifying
+individual meteorological variables independently, breaking their physical
+relationships. Despite these shortcomings, this method is still widely used
+because of its simple and flexible characteristics.
+Multiple morphing-based future weather
 generators have been developed over the decades to integrate climate change
@@
 climate. They consider two representative concentration pathway (RCP) emission
-scenarios, i.e. RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
+scenarios, i.e., RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
 Assessment Report (AR5). At the same time, both are commercial products, and the
@@
 To this end, this paper proposes a future weather generation method for BES
-based on CMIP6 ScenarioMIP climate scenarios, and develops a a free and
+based on CMIP6 ScenarioMIP climate scenarios, and develops a free and
 open-source tool epwshiftr. It incorporates open data from the latest CMIP6
@@
 #| eval = TRUE,
+#| out.width = "0.7\\textwidth",
+#| fig.env = "figure*",
 #| fig.cap = "Scenario design matrix for future climate prediction based on SSP
 #|   and RCP in ScenarioMIP\\citep{oneill2016scenario}"
-
-knitr::include_graphics("figures/ssp.png")
+knitr::include_graphics("figures/ssp-hires.png")
 ```
@@
 
-\begin{listing}
-\caption{Install epwshiftr}\label{lst:install}
-\includegraphics[width=\columnwidth]{figures/code-install.png}
-\end{listing}
+```{r}
+#| install,
+#| eval = FALSE,
+#| code.ref = "lst:install",
+#| code.cap = "Install epwshiftr"
+install.packages("epwshiftr")
+```
 
@@
 #| eval = TRUE,
+#| out.width = "0.7\\textwidth",
+#| fig.env = "figure*",
 #| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"
+knitr::include_graphics("figures/workflow-hires.png")
+```
 
-knitr::include_graphics("figures/workflow.png")
-```
+The epwshiftr package follows the Test-Driven Development (TDD) process. Around
+450 unit tests are carefully made, covering 94% of the codebase. They are
+automatically run on Windows, macOS, and Linux whenever changes are made in
+epwshiftr on CRAN and GitHub.
 
@@
 The *Query Module* provides an interface utilizing the RESTful API provided by
-ESGF and thus is capable of querying all CMIP6 GCM outputs based on various
+ESGF. It thus is capable of querying all CMIP6 GCM outputs based on various
 conditions, providing download links of NetCDF files. The query result will be
 processed into a data frame that contains 22 metadata that describes each
-output. Also, an output index is generated based on the query and is used to
+output. Also, an output index is generated based on the query to
 check the data integrity before extracting climate change data.
 
-Listing 2 demonstrates how to use the `index_cmip6_index` interface from the
-*Query Module*.
+Listing \ref{lst:index} demonstrates how to use the `index_cmip6_index`
+interface from the *Query Module*.
 
@@
 AWI-CM-1-1-MR GCM first run (r1i1p1f1) under SSP585 climate scenario from the
-ScenarioMIP activity for year 2050 and 2080. Also an output index file named
-"cmip6_index.csv" will be saved.
+ScenarioMIP activity for the year 2050 and 2080. Also, an output index file
+named "cmip6_index.csv" will be saved.
 
-\begin{listing}
-\caption{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
-\includegraphics[width=\columnwidth]{figures/code-index.png}
-\end{listing}
+```{r}
+#| lst-index,
+#| eval = FALSE,
+#| code.ref = "lst:index",
+#| code.cap = "Query ScenarioMIP outputs using the Query Module"
+# generate GCM output index
+idx <- init_cmip6_index(
+  # only consider ScenarioMIP activity
+  activity = "ScenarioMIP",
+
+  # output variables of interest
+  variable = c("tas", "hurs"),
+
+  # report frequency
+  frequency = "day",
+
+  # experiment name
+  experiment = "ssp585",
+
+  # GCM name
+  source = "AWI-CM-1-1-MR",
+
+  # variant,
+  variant = "r1i1p1f1",
+
+  # years of interest
+  years = c(2050, 2080),
+
+  # save result as an output index file
+  save = TRUE
+)
+```
 
@@
 #|   files"
-
 knitr::include_graphics("figures/db.png")
@@
 global attribute and manages the original big data of ScenarioMIP GCM climate
-change. Since the amount of data to extract from the global attributes in NetCDF
-is negligible compared to the total data volume of the time-series matrix, the
-computational load is small. It should be pointed out that CMIP6 does not
+change. The computational load is small since the amount of data to extract from
+the global attributes in NetCDF is negligible compared to the total data volume
+of the time-series matrix. It should be pointed out that CMIP6 does not
 require a specific calendar format for the time series GCM output. Various
-calendars exist, including the standard calendar, proleptic gregorian calendar,
+calendars exist, including the standard calendar, proleptic Gregorian calendar,
 365-day calendar, 366-day calendar, 360-day calendar, etc. Therefore, careful
 attention has been paid when converting the time range information obtained from
-ESGF and NetCDF files to ensure they are all transformed to the standard
+ESGF and NetCDF files to ensure they are all transformed into the standard
 calendar.
@@
 output index generated using the *Query Module.* This step is necessary as it maps
-the loaded files against index so that epwshiftr knows which case is complete
-and can be used for the next step.
+the loaded files against the index so that epwshiftr knows which case is
+complete and can be used for the next step.
 
-\begin{listing}
-\caption{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
-\includegraphics[width=\columnwidth]{figures/code-db.png}
-\end{listing}
+```{r}
+#| lst-db,
+#| eval = FALSE,
+#| code.ref = "lst:db",
+#| code.cap = "Summarize the GCM NetCDF files based on the output index"
+sm <- summary_database(
+  # where all the NetCDF files are
+  dir = getOption("epwshiftr.dir"),
+
+  # criteria for calculating completeness
+  by = c("source", "variable"),
+
+  # what to do for duplications
+  mult = "latest"
+)
+```
 
@@
 uniform standard method exists to calculate the distance between two points on a
-global grid. The common methods are: (a) Euler distance method, (b) Tunnel
-Distance method and (c) K-D tree algorithm. The Data Extraction Module uses the
+global grid. The common methods are: (a) the Euler distance method, (b) the Tunnel
+Distance method, and (c) the K-D tree algorithm. The Data Extraction Module uses the
 Euler distance method. Moreover, it also provides parameters to specify the
@@
 
-\begin{listing}
-\caption{Match the global grid points directly using an EPW file and extract raw GCM data}\label{lst:data}
-\includegraphics[width=\columnwidth]{figures/code-data.png}
-\end{listing}
-
 Listing \ref{lst:data} demonstrates how to use the `match_coord` interface from
@@
 meet the specified requirements, i.e., the maximum geographical distance between
-the matched grid points and selected location should be less than 0.5 degree,
-and only return the closest point. It also showcases the ability of directly
-using an EPW file as input for coordinate matching, as epwshiftr can parse the
+the matched grid points and selected location should be less than 0.5 degrees,
+and only return the closest point. It also showcases the ability to directly
+use an EPW file as input for coordinate matching, as epwshiftr can parse the
 geographical information stored in EPW files.
@@
 
+```{r}
+#| lst-data,
+#| eval = FALSE,
+#| code.ref = "lst:data",
+#| code.cap = "Match the global grid points directly using an EPW file and
+#|   extract raw GCM data"
+# use weather file distributed from
+# EnergyPlus v8.8 as an example
+epw <- eplusr::path_eplus_weather(
+  ver = 8.8,
+  file = "USA_CA_San.Francisco.Intl.AP.724940_TMY3.epw"
+)
+
+# extract matched grid coordinates
+coord <- match_coord(
+  epw,
+
+  # match distance less than 0.5 degrees
+  threshold = list(lon = 0.5, lat = 0.5),
+
+  # match at most 3 grid points
+  max_num = 3
+)
+
+# extract all data from matched grid points
+data <- extract_data(coord,
+  # specify the years to extract
+  years = c(2050, 2080)
+)
+```
+
 The size of the raw data extracted can be relatively big. For example, based on
@@
 climate variables from 2020 to 2100 from 4 climate scenarios and 11 GCMs, which
-is often close to, if not greater than, a normal PC's memory. For this reason,
-epwshiftr supports storing the original data in the fst format [@mark2022fst]
-with a super large compression ratio, which greatly reduces the content burden
+is often close to, if not greater than, a typical PC's memory. For this reason,
+epwshiftr supports storing the original data in the *fst* format [@mark2022fst]
+with a super large compression ratio, greatly reducing the content burden
 required for calculation. Still taking the above situation as an example, if the
@@
 
+To avoid unrealistic results, the *Morphing Module* has taken extra data
+validation and calculation steps, including but not limited to:
+
+* Warnings are generated if there are any missing values in the input EPW and
+  GCM data.
+* Unit conversions between data of EPW and GCM are automatically performed using
+  the units [@pebesma2016measurement] R package, e.g. all temperature data have
+  been converted to Celsius before calculation.
+* Calculation of dew point temperature is performed based on dry-bulb
+  temperature and relative humidity using the psychrolib [@meyer2019psychrolib]
+  R package.
+* Input values of relative humidity that exceed 100% will be reset to 100%.
+* A threshold value is set for the stretch factor ($\alpha$), i.e. monthly-mean
+  fractional change, when performing morphing operations. The default value is
+  set to `3`. If the absolute $\alpha$ exceeds this threshold value, warnings
+  are issued to suggest users further investigate the input data before
+  continuing. Moreover, the morphing method will use the shift factor ($\Delta x$)
+  to to avoid unrealistic morphed values.
+
+Besides the efforts above, the *Morphing Module* always returns the calculated
+$\Delta x$ and $\alpha$ values in dedicated columns, which provides
+opportunities for detailed examination and custom statistical analyses.
+
 At the same time, when generating EPW files, average processing can also be
@@
 the *Morphing Module* and the `future_epw` interface from the *EPW Generation
-Module* to perform morphing on the baseline EPW data and raw GCM data, and
+Module* to perform morphing on the baseline EPW data and raw GCM data and
 create future EPW files based on the GCM source, climate scenarios and time
-interval. All EPW files will be saved into a seprate folder.
+interval. All EPW files will be saved into a separate folder.
 
-\begin{listing}
-\caption{Perform morphing and generate future EPWs}\label{lst:epw}
-\includegraphics[width=\columnwidth]{figures/code-epw.png}
-\end{listing}
+```{r}
+#| lst-epw,
+#| eval = FALSE,
+#| code.ref = "lst:epw",
+#| code.cap = "Perform morphing and generate future EPWs"
+# perform morphing
+morphed <- morphing_epw(data,
+  # years of interest
+  years = c(2050, 2080)
+)
+
+# create future EPWs
+epws <- future_epw(
+  morphed,
+
+  # how to group the output files
+  by = c("source", "experiment", "interval"),
+
+  # where to save all generated EPWs
+  dir = tempdir(),
+
+  # create folders for each group
+  separate = TRUE,
+
+  # overwrite existing files
+  overwrite = TRUE
+)
+```
+
+Currently, epwshiftr only supports the morphing method. But the `morphing_epw`
+interface provides parameters to modify which factors should be used for each
+meteorological variable, with meaningful defaults value given. For example,
+radiation-related variables are, by default, morphed using the stretch factor,
+avoiding unrealistic positive values at nighttime. The modular design pattern of
+epwshiftr makes it decouple the data structure and the actual extrapolation
+algorithm used. We are happy to explore the feasibility of supporting
+alternative extrapolation algorithms in the future.
 
@@
 and automatically process significant amounts of climate change model data
-worldwide. This tool will significantly save the time and cost of obtaining
-future weather data and thus can support the analysis of future building heating
-and air-conditioning demand, energy consumption, and carbon emissions.
+worldwide. We hope this tool will significantly save the time and cost of
+obtaining future weather data. It thus can support the analysis of future
+building heating and air-conditioning demand, energy consumption, and carbon
+emissions.
 

### 2023-06-09 full-paper/paper.tex
paper: address reviewer comments

@@
 % add caption for codes
-\DeclareNewFloatType{Code}{placement=h, fileext=code, name=Listing}
-\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}
-\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}
-
-% add a custom float environment for listing in figure format
-\DeclareFloatingEnvironment[
-    fileext=los,
-    listname={List of Listings},
-    name=Listing,
-    placement=tbhp
-]{listing}
+\DeclareNewFloatType{code}{placement=h, fileext=code, name=Listing}
+\captionsetup[code]{aboveskip=10pt, belowskip=1pt}
 
@@
     commandchars=\\\{\},
-    fontsize=\scriptsize,
+    fontsize=\normalsize,
     numbers=left,
@@
 }
-\newenvironment{Shaded}{\captionof{Code}{} \begin{mdframed}[skipabove=0pt]}{\end{mdframed}}
+
+\newenvironment{Shaded}{\begin{mdframed}[skipabove=0pt]}{\end{mdframed}}
 \mdfsetup{%
@@
 method, which utilizes the Global Climate Model (GCM) output, is a relatively
-simple and reliable method for future weather data prediction and is widely
+simple method for future weather data prediction and is widely
 used in current research/tools. However, existing weather generators typically
@@
 conditions of BES and directly affect the results \citep{bhandari2012evaluation}.
-Therefore, it is necessary to use further weather data considering climate
+Therefore, it is necessary to use future weather data considering climate
 change for the design and performance evaluation of new and existing buildings
@@
 creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
-the morphing method, a relatively simple and reliable statistical downscaling
+the morphing method, a relatively simple statistical downscaling
 method. It is based on the future climate change data predicted by the Global
@@
 year (TMY). Morphing can capture the average future weather conditions from GCM
-while preserving historical weather sequences. Multiple future weather
+while preserving historical weather sequences. It requires low computational
+power, making it possible to create many weather files from worldwide locations.
+However, morphing may under- or overestimate climate change impacts because of
+the lacking of ability to capture future extreme weather conditions and
+potential differences in the reference time frame of the TMY and GCM data
+\citep{moazami2019impacts}.
+Moreover, careful consideration should be given to morphing when modifying
+individual meteorological variables independently, breaking their physical
+relationships. Despite these shortcomings, this method is still widely used
+because of its simple and flexible characteristics.
+Multiple morphing-based future weather
 generators have been developed over the decades to integrate climate change
@@
 climate. They consider two representative concentration pathway (RCP) emission
-scenarios, i.e.~RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
+scenarios, i.e., RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
 Assessment Report (AR5). At the same time, both are commercial products, and the
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{figures/ssp} \caption{Scenario design matrix for future climate prediction based on SSP  and RCP in ScenarioMIP\citep{oneill2016scenario}}\label{fig:ssp}
-\end{figure}
+\begin{figure*}
+\includegraphics[width=0.7\textwidth]{figures/ssp-hires} \caption{Scenario design matrix for future climate prediction based on SSP  and RCP in ScenarioMIP\citep{oneill2016scenario}}\label{fig:ssp}
+\end{figure*}
 
@@
 
-\begin{listing}
-\caption{Install epwshiftr}\label{lst:install}
-\includegraphics[width=\columnwidth]{figures/code-install.png}
-\end{listing}
+\captionof{code}{Install epwshiftr}\label{lst:install}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{install.packages}\NormalTok{(}\StringTok{"epwshiftr"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{figures/workflow} \caption{The primary process of using epwshiftr to generate EPW files for future weather}\label{fig:workflow}
-\end{figure}
+\begin{figure*}
+\includegraphics[width=0.7\textwidth]{figures/workflow-hires} \caption{The primary process of using epwshiftr to generate EPW files for future weather}\label{fig:workflow}
+\end{figure*}
+
+The epwshiftr package follows the Test-Driven Development (TDD) process. Around
+450 unit tests are carefully made, covering 94\% of the codebase. They are
+automatically run on Windows, macOS, and Linux whenever changes are made in
+epwshiftr on CRAN and GitHub.
 
@@
 The \emph{Query Module} provides an interface utilizing the RESTful API provided by
-ESGF and thus is capable of querying all CMIP6 GCM outputs based on various
+ESGF. It thus is capable of querying all CMIP6 GCM outputs based on various
 conditions, providing download links of NetCDF files. The query result will be
 processed into a data frame that contains 22 metadata that describes each
-output. Also, an output index is generated based on the query and is used to
+output. Also, an output index is generated based on the query to
 check the data integrity before extracting climate change data.
 
-Listing 2 demonstrates how to use the \texttt{index\_cmip6\_index} interface from the
-\emph{Query Module}.
+Listing \ref{lst:index} demonstrates how to use the \texttt{index\_cmip6\_index}
+interface from the \emph{Query Module}.
 
@@
 AWI-CM-1-1-MR GCM first run (r1i1p1f1) under SSP585 climate scenario from the
-ScenarioMIP activity for year 2050 and 2080. Also an output index file named
-``cmip6\_index.csv'' will be saved.
+ScenarioMIP activity for the year 2050 and 2080. Also, an output index file
+named ``cmip6\_index.csv'' will be saved.
 
-\begin{listing}
-\caption{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
-\includegraphics[width=\columnwidth]{figures/code-index.png}
-\end{listing}
+\captionof{code}{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# generate GCM output index}
+\NormalTok{idx }\OtherTok{\textless{}{-}} \FunctionTok{init\_cmip6\_index}\NormalTok{(}
+  \CommentTok{\# only consider ScenarioMIP activity}
+  \AttributeTok{activity =} \StringTok{"ScenarioMIP"}\NormalTok{,}
+
+  \CommentTok{\# output variables of interest}
+  \AttributeTok{variable =} \FunctionTok{c}\NormalTok{(}\StringTok{"tas"}\NormalTok{, }\StringTok{"hurs"}\NormalTok{),}
+
+  \CommentTok{\# report frequency}
+  \AttributeTok{frequency =} \StringTok{"day"}\NormalTok{,}
+
+  \CommentTok{\# experiment name}
+  \AttributeTok{experiment =} \StringTok{"ssp585"}\NormalTok{,}
+
+  \CommentTok{\# GCM name}
+  \AttributeTok{source =} \StringTok{"AWI{-}CM{-}1{-}1{-}MR"}\NormalTok{,}
+
+  \CommentTok{\# variant,}
+  \AttributeTok{variant =} \StringTok{"r1i1p1f1"}\NormalTok{,}
+
+  \CommentTok{\# years of interest}
+  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{),}
+
+  \CommentTok{\# save result as an output index file}
+  \AttributeTok{save =} \ConstantTok{TRUE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 output index generated using the \emph{Query Module.} This step is necessary as it maps
-the loaded files against index so that epwshiftr knows which case is complete
-and can be used for the next step.
+the loaded files against the index so that epwshiftr knows which case is
+complete and can be used for the next step.
 
-\begin{listing}
-\caption{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
-\includegraphics[width=\columnwidth]{figures/code-db.png}
-\end{listing}
+\captionof{code}{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{sm }\OtherTok{\textless{}{-}} \FunctionTok{summary\_database}\NormalTok{(}
+  \CommentTok{\# where all the NetCDF files are}
+  \AttributeTok{dir =} \FunctionTok{getOption}\NormalTok{(}\StringTok{"epwshiftr.dir"}\NormalTok{),}
+
+  \CommentTok{\# criteria for calculating completeness}
+  \AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"source"}\NormalTok{, }\StringTok{"variable"}\NormalTok{),}
+
+  \CommentTok{\# what to do for duplications}
+  \AttributeTok{mult =} \StringTok{"latest"}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\begin{listing}
-\caption{Match the global grid points directly using an EPW file and extract raw GCM data}\label{lst:data}
-\includegraphics[width=\columnwidth]{figures/code-data.png}
-\end{listing}
-
 Listing \ref{lst:data} demonstrates how to use the \texttt{match\_coord} interface from
@@
 
+\captionof{code}{Match the global grid points directly using an EPW file and  extract raw GCM data}\label{lst:data}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# use weather file distributed from}
+\CommentTok{\# EnergyPlus v8.8 as an example}
+\NormalTok{epw }\OtherTok{\textless{}{-}}\NormalTok{ eplusr}\SpecialCharTok{::}\FunctionTok{path\_eplus\_weather}\NormalTok{(}
+  \AttributeTok{ver =} \FloatTok{8.8}\NormalTok{,}
+  \AttributeTok{file =} \StringTok{"USA\_CA\_San.Francisco.Intl.AP.724940\_TMY3.epw"}
+\NormalTok{)}
+
+\CommentTok{\# extract matched grid coordinates}
+\NormalTok{coord }\OtherTok{\textless{}{-}} \FunctionTok{match\_coord}\NormalTok{(}
+\NormalTok{  epw,}
+
+  \CommentTok{\# match distance less than 0.5 degrees}
+  \AttributeTok{threshold =} \FunctionTok{list}\NormalTok{(}\AttributeTok{lon =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{lat =} \FloatTok{0.5}\NormalTok{),}
+
+  \CommentTok{\# match at most 3 grid points}
+  \AttributeTok{max\_num =} \DecValTok{3}
+\NormalTok{)}
+
+\CommentTok{\# extract all data from matched grid points}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{extract\_data}\NormalTok{(coord,}
+  \CommentTok{\# specify the years to extract}
+  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{)}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
 The size of the raw data extracted can be relatively big. For example, based on
@@
 climate variables from 2020 to 2100 from 4 climate scenarios and 11 GCMs, which
-is often close to, if not greater than, a normal PC's memory. For this reason,
-epwshiftr supports storing the original data in the fst format \citep{mark2022fst}
-with a super large compression ratio, which greatly reduces the content burden
+is often close to, if not greater than, a typical PC's memory. For this reason,
+epwshiftr supports storing the original data in the \emph{fst} format \citep{mark2022fst}
+with a super large compression ratio, greatly reducing the content burden
 required for calculation. Still taking the above situation as an example, if the
@@
 
+To avoid unrealistic results, the \emph{Morphing Module} has taken extra data
+validation and calculation steps, including but not limited to:
+
+\begin{itemize}
+\tightlist
+\item
+  Warnings are generated if there are any missing values in the input EPW and
+  GCM data.
+\item
+  Unit conversions between data of EPW and GCM are automatically performed using
+  the units \citep{pebesma2016measurement} R package, e.g.~all temperature data have
+  been converted to Celsius before calculation.
+\item
+  Calculation of dew point temperature is performed based on dry-bulb
+  temperature and relative humidity using the psychrolib \citep{meyer2019psychrolib}
+  R package.
+\item
+  Input values of relative humidity that exceed 100\% will be reset to 100\%.
+\item
+  A threshold value is set for the stretch factor (\(\alpha\)), i.e.~monthly-mean
+  fractional change, when performing morphing operations. The default value is
+  set to \texttt{3}. If the absolute \(\alpha\) exceeds this threshold value, warnings
+  are issued to suggest users further investigate the input data before
+  continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
+  to to avoid unrealistic morphed values.
+\end{itemize}
+
+Besides the efforts above, the \emph{Morphing Module} always returns the calculated
+\(\Delta x\) and \(\alpha\) values in dedicated columns, which provides
+opportunities for detailed examination and custom statistical analyses.
+
 At the same time, when generating EPW files, average processing can also be
@@
 the \emph{Morphing Module} and the \texttt{future\_epw} interface from the \emph{EPW Generation
-Module} to perform morphing on the baseline EPW data and raw GCM data, and
+Module} to perform morphing on the baseline EPW data and raw GCM data and
 create future EPW files based on the GCM source, climate scenarios and time
-interval. All EPW files will be saved into a seprate folder.
+interval. All EPW files will be saved into a separate folder.
 
-\begin{listing}
-\caption{Perform morphing and generate future EPWs}\label{lst:epw}
-\includegraphics[width=\columnwidth]{figures/code-epw.png}
-\end{listing}
+\captionof{code}{Perform morphing and generate future EPWs}\label{lst:epw}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# perform morphing}
+\NormalTok{morphed }\OtherTok{\textless{}{-}} \FunctionTok{morphing\_epw}\NormalTok{(data,}
+  \CommentTok{\# years of interest}
+  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{)}
+\NormalTok{)}
+
+\CommentTok{\# create future EPWs}
+\NormalTok{epws }\OtherTok{\textless{}{-}} \FunctionTok{future\_epw}\NormalTok{(}
+\NormalTok{  morphed,}
+
+  \CommentTok{\# how to group the output files}
+  \AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"source"}\NormalTok{, }\StringTok{"experiment"}\NormalTok{, }\StringTok{"interval"}\NormalTok{),}
+
+  \CommentTok{\# where to save all generated EPWs}
+  \AttributeTok{dir =} \FunctionTok{tempdir}\NormalTok{(),}
+
+  \CommentTok{\# create folders for each group}
+  \AttributeTok{separate =} \ConstantTok{TRUE}\NormalTok{,}
+
+  \CommentTok{\# overwrite existing files}
+  \AttributeTok{overwrite =} \ConstantTok{TRUE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
+interface provides parameters to modify which factors should be used for each
+meteorological variable, with meaningful defaults value given. For example,
+radiation-related variables are, by default, morphed using the stretch factor,
+avoiding unrealistic positive values at nighttime. The modular design pattern of
+epwshiftr makes it decouple the data structure and the actual extrapolation
+algorithm used. We are happy to explore the feasibility of supporting
+alternative extrapolation algorithms in the future.
 

### 2023-06-09 full-paper/reviews/1st-round-resp.Rmd
paper: add response to reviewers

---
output:
  bookdown::pdf_document2:
    template: ../template/revresp.tex
    citation_package: natbib
    keep_tex: true

date: "2023-06-09"
id: 1612
---

# Response to the reviewers {-}

Dear Reviewers,

Thank you for giving me the opportunity to submit a revised draft of my
manuscript titled *Epwshiftr: incorporating open data of climate change
prediction into building performance simulation for future adaptation and
mitigation*. We appreciate the time and effort that you have dedicated to
providing valuable feedback and insightful comments on our work. We have been
able to incorporate changes to reflect most of the suggestions and have
highlighted the changes within the uploaded manuscript.

Below is a point-by-point response to the reviewers' comments and concerns.

```{=latex}
\reviewersection
```

:::{.point data-latex=""}
This paper developed a free open-source future weather generator epwshiftr,
which can generate future weather data for 11 meteorological variables.
:::

:::{.reply data-latex=""}
Thank you for the comments. We hope epwshiftr can ease the data-processing
burden and reduce the costs of energy modelers when preparing future weather
files for assessing climate change impacts on building energy performance.
:::

```{=latex}
\reviewersection
```

Epwshiftr appears to be a useful tool for modelers investigating likely
performance of buildings in the future.

:::{.point data-latex=""}
The format and writing quality of the paper is acceptable once minor errors are
corrected. I noticed as least one incorrect word usage ("further" instead of
"future"). Please carefully proof-read the paper.
:::

:::{.reply data-latex=""}
Thank you for pointing this out. The typo has been corrected. The manuscript has
been proofread with spelling and grammatical errors corrected.
:::

:::{.point data-latex=""}
Figures 1 and 2 are both unreadable in a printout of the paper. They are not
particularly clear even when viewing the PDF at high magnification. The listings
are fuzzy; listings 4 and 5 are also too small. The manuscript is significantly
shorter than the 8 page limit, so space is available to enlarge and clarify
these items.
:::

:::{.reply data-latex=""}
Thank you for the suggestions.

The manuscript has been rewritten using BS2023 \LaTeX template for better image
and listing formatting.
The image file of Figure 1 and 2 have been replaced with high-resolution ones.
Also, both have been enlarged and placed in full page width.

In the original draft, all listings were screenshots of code snippets in small sizes.
Now we replace all of them by rewriting using \LaTeX listings. Clarifications of
code have been added as comments in each listing. The fonts have been enlarged
to make sure they are readable in the printout version.
:::

:::{.point data-latex=""}
You refer to the morphing method as "reliable". I am not sure there is
consensus on that. Morphing modifies individual weather items independently and
may not preserve physically realistic relationships among them. Further,
unconstrained morphing can produce physically impossible values, such as wet
bulb temperature greater than dry bulb temperature. Finally, morphing does not
capture time-dependent effects such as concentration of temperature increases in
nighttime hours. You should amplify your discussion of how morphing is
implemented.
:::

:::{.reply data-latex=""}
\label{rp:validation}
Thank you for the insightful comments and suggestions.

We have changed the description of the morphing method in both the Abstract and
Introduction section. Both advantages and disadvantages of it have been added in
the Introduction section:

> Morphing can capture the average future weather conditions from GCM while
> preserving historical weather sequences. It requires low computational power,
> making it possible to create many weather files from worldwide locations.
> However, morphing may under- or overestimate climate change impacts because of
> the lacking of ability to capture future extreme weather conditions and
> potential differences in the reference time frame of the TMY and GCM data
> (Moazami et al., 2019). Moreover, careful consideration should be given to
> morphing when modifying individual meteorological variables independently,
> breaking their physical relationships. Despite these shortcomings, this method
> is still widely used because of its simple and flexible characteristics.

Description about how the morphing method is implemented in epwshiftr has also
been added:

> To avoid unrealistic results, the *Morphing Module* has taken extra data
> validation and calculation steps, including but not limited to:
>
> * Warnings are generated if there are any missing values in the input EPW and
>   GCM data.
> * Unit conversions between data of EPW and GCM are automatically performed using
>   the units (Pebesma et al., 2016) R package, e.g. all temperature data have
>   been converted to Celsius before calculation.
> * Calculation of dew point temperature is performed based on dry-bulb
>   temperature and relative humidity using the psychrolib (Meyer and Thevenard,
>   2019) R package.
> * Input values of relative humidity that exceed 100% will be reset to 100%.
> * A threshold value is set for the stretch factor ($\alpha$), i.e. monthly-mean
>   fractional change, when performing morphing operations. The default value is
>   set to `3`. If the absolute $\alpha$ exceeds this threshold value, warnings
>   are issued to suggest users further investigate the input data before
>   continuing. Moreover, the morphing method will use the shift factor ($\Delta x$)
>   to to avoid unrealistic morphed values.
:::

:::{.point data-latex=""}
Further, you should comment on the adaptability of your framework to support
alternative extrapolation algorithms.
:::

:::{.reply data-latex=""}
Thank for the suggestion.

Currently, epwshiftr only supports the morphing method. We are happy to explore
the feasibility of supporting alternative extrapolation algorithms in the
future. Clarifications have also been added in the *Morphing Module* section:

> Currently, epwshiftr only supports the morphing method. But the `morphing_epw`
> interface provides parameters to modify which factors should be used for each
> meteorological variable, with meaningful defaults value given. For example,
> radiation-related variables are, by default, morphed using the stretch factor,
> avoiding unrealistic positive values at nighttime. The modular design pattern of
> epwshiftr makes it decouple the data structure and the actual extrapolation
> algorithm used. We are happy to explore the feasibility of supporting
> alternative extrapolation algorithms in the future.
:::

:::{.point data-latex=""}
In addition, it would be helpful to provide at least general information on
testing and validation. Have simulation results been compared for studies done
with epwshiftr weather data to those conducted with some of the other future
weather methods you cite? Is the NetCDF data reliable and what happens when it
is not? Can potential users be confident that epwshiftr will "do the job"?
:::

:::{.reply data-latex=""}
Thank you for the comments and suggestions.

We take seriously about code correctness. For details about the test coverage,
please see epwshiftr code coverage
report^[https://app.codecov.io/gh/ideas-lab-nus/epwshiftr?branch=master]. A
description of the code quality assurance has been added in the 3rd section:

> The epwshiftr package follows the Test-Driven Development (TDD) process. Around
> 450 unit tests are carefully made, covering 94% of the codebase. They are
> automatically run on Windows, macOS, and Linux whenever changes are made in
> epwshiftr on CRAN and GitHub.

In terms of validation, besides data validation steps in epwshiftr itself
described in Response \ref{rp:validation}, epwshiftr uses Defensive Programming
pattern^[https://en.wikipedia.org/wiki/Defensive_programming]. Careful efforts
have been made to validate user inputs including data types, value length and
range, ESGF data node availability, NetCDF file accessibility, etc., avoiding
common mistakes before computation.

epwshiftr stores and returns data in a consistent tidy format, making it easy
for users to examine the returned data of each module further. In terms of the
calculated morphing factors, a description of the structure of the returned data
from the *Morphing Module* is also added:

> Besides the efforts above, the *Morphing Module* always returns the calculated
> $\Delta x$ and $\alpha$ values in dedicated columns, which provides
> opportunities for detailed examination and custom statistical analyses.
:::

### 2023-06-09 full-paper/reviews/1st-round-resp.tex
paper: add response to reviewers

% Source: https://zenkelab.org/resources/latex-rebuttal-response-to-reviewers-template/
% Modified with minor justifications by Hongyuan Jia
%
% Original License:
%
% LaTeX rebuttal letter example.
%
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
%
% Licensed under cc by-sa 3.0 with attribution required.
% See https://creativecommons.org/licenses/by-sa/3.0/
% and https://stackoverflow.blog/2009/06/25/attribution-required/

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{xcolor}

\usepackage[hidelinks]{hyperref}

% import Eq and Section references from the main manuscript where needed
% \usepackage{xr}
% \externaldocument{../paper}

% package needed for optional arguments
\usepackage{xifthen}
% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent
    {\textbf{Reviewer~Point~\thepoint} } ---~#1\par }

\newenvironment{reply}
   {\medskip \noindent \textbf{Reply}:\  }
   {\medskip }

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
    \ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
    \medskip \end{sf}}

% change the font color in quote
\AddToHook{env/quote/begin}{\small\color{blue!70}}

% for pandoc generated list
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}
\hypertarget{response-to-the-reviewers}{%
\section*{Response to the reviewers}\label{response-to-the-reviewers}}
\addcontentsline{toc}{section}{Response to the reviewers}

Dear Reviewers,

Thank you for giving me the opportunity to submit a revised draft of my
manuscript titled \emph{Epwshiftr: incorporating open data of climate change
prediction into building performance simulation for future adaptation and
mitigation}. We appreciate the time and effort that you have dedicated to
providing valuable feedback and insightful comments on our work. We have been
able to incorporate changes to reflect most of the suggestions and have
highlighted the changes within the uploaded manuscript.

Below is a point-by-point response to the reviewers' comments and concerns.

\reviewersection

\begin{point}
This paper developed a free open-source future weather generator epwshiftr,
which can generate future weather data for 11 meteorological variables.

\end{point}

\begin{reply}
Thank you for the comments. We hope epwshiftr can ease the data-processing
burden and reduce the costs of energy modelers when preparing future weather
files for assessing climate change impacts on building energy performance.

\end{reply}

\reviewersection

Epwshiftr appears to be a useful tool for modelers investigating likely
performance of buildings in the future.

\begin{point}
The format and writing quality of the paper is acceptable once minor errors are
corrected. I noticed as least one incorrect word usage (``further'' instead of
``future''). Please carefully proof-read the paper.

\end{point}

\begin{reply}
Thank you for pointing this out. The typo has been corrected. The manuscript has
been proofread with spelling and grammatical errors corrected.

\end{reply}

\begin{point}
Figures 1 and 2 are both unreadable in a printout of the paper. They are not
particularly clear even when viewing the PDF at high magnification. The listings
are fuzzy; listings 4 and 5 are also too small. The manuscript is significantly
shorter than the 8 page limit, so space is available to enlarge and clarify
these items.

\end{point}

\begin{reply}
Thank you for the suggestions.

The manuscript has been rewritten using BS2023 \LaTeX template for better image
and listing formatting.
The image file of Figure 1 and 2 have been replaced with high-resolution ones.
Also, both have been enlarged and placed in full page width.

In the original draft, all listings were screenshots of code snippets in small sizes.
Now we replace all of them by rewriting using \LaTeX listings. Clarifications of
code have been added as comments in each listing. The fonts have been enlarged
to make sure they are readable in the printout version.

\end{reply}

\begin{point}
You refer to the morphing method as ``reliable''. I am not sure there is
consensus on that. Morphing modifies individual weather items independently and
may not preserve physically realistic relationships among them. Further,
unconstrained morphing can produce physically impossible values, such as wet
bulb temperature greater than dry bulb temperature. Finally, morphing does not
capture time-dependent effects such as concentration of temperature increases in
nighttime hours. You should amplify your discussion of how morphing is
implemented.

\end{point}

\begin{reply}

\label{rp:validation}
Thank you for the insightful comments and suggestions.

We have changed the description of the morphing method in both the Abstract and
Introduction section. Both advantages and disadvantages of it have been added in
the Introduction section:

\begin{quote}
Morphing can capture the average future weather conditions from GCM while
preserving historical weather sequences. It requires low computational power,
making it possible to create many weather files from worldwide locations.
However, morphing may under- or overestimate climate change impacts because of
the lacking of ability to capture future extreme weather conditions and
potential differences in the reference time frame of the TMY and GCM data
(Moazami et al., 2019). Moreover, careful consideration should be given to
morphing when modifying individual meteorological variables independently,
breaking their physical relationships. Despite these shortcomings, this method
is still widely used because of its simple and flexible characteristics.
\end{quote}

Description about how the morphing method is implemented in epwshiftr has also
been added:

\begin{quote}
To avoid unrealistic results, the \emph{Morphing Module} has taken extra data
validation and calculation steps, including but not limited to:

\begin{itemize}
\tightlist
\item
  Warnings are generated if there are any missing values in the input EPW and
  GCM data.
\item
  Unit conversions between data of EPW and GCM are automatically performed using
  the units (Pebesma et al., 2016) R package, e.g.~all temperature data have
  been converted to Celsius before calculation.
\item
  Calculation of dew point temperature is performed based on dry-bulb
  temperature and relative humidity using the psychrolib (Meyer and Thevenard,

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi})}
  \setcounter{enumi}{2018}
  \tightlist
  \item
    R package.
  \end{enumerate}
\item
  Input values of relative humidity that exceed 100\% will be reset to 100\%.
\item
  A threshold value is set for the stretch factor (\(\alpha\)), i.e.~monthly-mean
  fractional change, when performing morphing operations. The default value is
  set to \texttt{3}. If the absolute \(\alpha\) exceeds this threshold value, warnings
  are issued to suggest users further investigate the input data before
  continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
  to to avoid unrealistic morphed values.
\end{itemize}
\end{quote}

\end{reply}

\begin{point}
Further, you should comment on the adaptability of your framework to support
alternative extrapolation algorithms.

\end{point}

\begin{reply}

Thank for the suggestion.

Currently, epwshiftr only supports the morphing method. We are happy to explore
the feasibility of supporting alternative extrapolation algorithms in the
future. Clarifications have also been added in the \emph{Morphing Module} section:

\begin{quote}
Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
interface provides parameters to modify which factors should be used for each
meteorological variable, with meaningful defaults value given. For example,
radiation-related variables are, by default, morphed using the stretch factor,
avoiding unrealistic positive values at nighttime. The modular design pattern of
epwshiftr makes it decouple the data structure and the actual extrapolation
algorithm used. We are happy to explore the feasibility of supporting
alternative extrapolation algorithms in the future.
\end{quote}

\end{reply}

\begin{point}
In addition, it would be helpful to provide at least general information on
testing and validation. Have simulation results been compared for studies done
with epwshiftr weather data to those conducted with some of the other future
weather methods you cite? Is the NetCDF data reliable and what happens when it
is not? Can potential users be confident that epwshiftr will ``do the job''?

\end{point}

\begin{reply}

Thank you for the comments and suggestions.

We take seriously about code correctness. For details about the test coverage,
please see epwshiftr code coverage
report\footnote{\url{https://app.codecov.io/gh/ideas-lab-nus/epwshiftr?branch=master}}. A
description of the code quality assurance has been added in the 3rd section:

\begin{quote}
The epwshiftr package follows the Test-Driven Development (TDD) process. Around
450 unit tests are carefully made, covering 94\% of the codebase. They are
automatically run on Windows, macOS, and Linux whenever changes are made in
epwshiftr on CRAN and GitHub.
\end{quote}

In terms of validation, besides data validation steps in epwshiftr itself
described in Response \ref{rp:validation}, epwshiftr uses Defensive Programming
pattern\footnote{\url{https://en.wikipedia.org/wiki/Defensive_programming}}. Careful efforts
have been made to validate user inputs including data types, value length and
range, ESGF data node availability, NetCDF file accessibility, etc., avoiding
common mistakes before computation.

epwshiftr stores and returns data in a consistent tidy format, making it easy
for users to examine the returned data of each module further. In terms of the
calculated morphing factors, a description of the structure of the returned data
from the \emph{Morphing Module} is also added:

\begin{quote}
Besides the efforts above, the \emph{Morphing Module} always returns the calculated
\(\Delta x\) and \(\alpha\) values in dedicated columns, which provides
opportunities for detailed examination and custom statistical analyses.
\end{quote}

\end{reply}
\end{document}

### 2023-06-15 R/latexdiff.R
workflow: use targets to manage build workflow

@@ -1,0 +1,120 @@
+latexdiff <- function(ref_old, ref_new, rmd, out = "diff.tex", clean = TRUE) {
+    tex <- rmd
+    no_ext <- tools::file_path_sans_ext(tex)
+    if (tools::file_ext(tex) != "tex") tex <- paste0(no_ext, ".tex")
+
+    if (!file.exists(tex)) {
+        stop(sprintf("Failed to find LaTeX input '%s'.", normalizePath(tex, mustWork = FALSE)))
+    }
+
+    if (Sys.which("latexdiff-vc") == "") {
+        message(
+            "Failed to find 'latexdiff-vc'. ",
+            "Trying to install using 'tinytex::tlmgr_install(\"latexdiff\")"
+        )
+        tinytex::tlmgr_install("latexdiff")
+    }
+
+    processx::run(
+        "latexdiff-vc",
+        c(
+            "--git", "--force",
+            "-r", ref_old, "-r", ref_new,
+            tex
+        )
+    )
+
+    # remove temporary files generated by latexdiff
+    if (clean) {
+        unlink(list.files(
+            dirname(tex),
+            sprintf("%s-((old)|(new))tmp-\\d+\\.tex", basename(no_ext)),
+            full.names = TRUE
+        ))
+    }
+
+    diff <- sprintf("%s-diff%s-%s.tex", no_ext, ref_old, ref_new)
+    if (!file.exists(diff)) {
+        stop("'latexdiff' failed to generate the TeX diff file.")
+    }
+
+    out <- file.path(dirname(no_ext), out)
+    stopifnot(file.rename(diff, out))
+    out
+}
+
+render_diff <- function(rmd, diff, ref_old, ref_new) {
+    if (fs::is_absolute_path(rmd)) {
+        stop("'rmd' should be a relative path.")
+    }
+
+    if (fs::is_absolute_path(diff)) {
+        stop("'diff' should be a relative path.")
+    }
+
+    # make sure rmd and diff are in the same root folder
+    if (fs::path_common(c(rmd, diff)) == "") {
+        stop("Please make sure 'rmd' and 'diff' share the same root folder.")
+    }
+
+    # create a temporary folder to store data
+    dir <- tempfile("latexdiff")
+    dir.create(dir)
+
+    # copy whole working directory to the temporary folder
+    stopifnot(all(
+        file.copy(list.files(all.files = TRUE, no.. = TRUE), dir,
[…]

### 2023-06-15 R/rmd.R

@@ -1,0 +1,59 @@
+path_rmd_root <- function(path, rmd) {
+    if (!length(path)) return()
+    fs::path_rel(file.path(dirname(rmd), path))
+}
+
+rmd_deps <- function(rmd) {
+    c(rmd_deps_img(rmd), rmd_deps_tmpl(rmd), rmd_deps_bib(rmd))
+}
+
+rmd_deps_bib <- function(rmd) {
+    # read yaml header
+    yaml <- rmarkdown::yaml_front_matter(rmd)
+
+    # extract bibliography file
+    path_rmd_root(yaml$bibliography, rmd)
+}
+
+rmd_deps_tmpl <- function(rmd) {
+    # read yaml header
+    yaml <- rmarkdown::yaml_front_matter(rmd)
+
+    # extract template
+    tmpl <- path_rmd_root(unlist(lapply(yaml$output, .subset, "template")), rmd)
+
+    # extract bst for LaTeX template
+    l <- readLines(tmpl, warn = FALSE)
+    re <- "^\\s*\\\\bibliographystyle\\s*{\\s*(.+)\\s*}"
+    m <- regmatches(l, regexec(re, l, perl = TRUE))
+    m <- m[lengths(m) == 2L]
+
+    bst <- NULL
+    if (length(m)) {
+        f <- paste0(vapply(m[lengths(m) == 2L], .subset2, "", 2L), ".bst")
+        bst <- path_rmd_root(f, rmd)
+    }
+
+    c(tmpl, bst)
+}
+
+rmd_deps_img <- function(rmd) {
+    re <- "(?:knitr::)?include_graphics\\((['\"])(.+)\\g{-2}\\)"
+    l <- readLines(rmd, warn = FALSE)
+    m <- regmatches(l, regexec(re, l, perl = TRUE))
+    f <- vapply(m[lengths(m) == 3L], .subset2, "", 3L)
+    path_rmd_root(f[f != ""], rmd)
+}
+
+render_rmd <- function(rmd, envir = parent.frame()) {
+    # read yaml header
+    yaml <- rmarkdown::yaml_front_matter(rmd)
+
+    out <- rmarkdown::render(rmd, "all", envir = envir)
+
+    if (unlist(lapply(yaml$output, .subset, "keep_tex"))) {
+        out <- c(out, paste0(tools::file_path_sans_ext(out[1]), ".tex"))
+    }
+
[…]

### 2023-06-15 _targets.R

@@ -1,0 +1,24 @@
+library(targets)
+library(tarchetypes)
+
+tar_source("R")
+
+list(
+    tar_target(dir_paper, "full-paper"),
+
+    # render full paper
+    tar_file(rmd_paper, file.path(dir_paper, "paper.Rmd")),
+    tar_file(deps_paper, rmd_deps(rmd_paper)),
+    tar_change(pdf_paper, render_rmd(rmd_paper), deps_paper, format = "file"),
+
+    # render 1st round response to reviewer comments
+    tar_file(rmd_1st_resp, file.path(dir_paper, "reviews", "1st-round-resp.Rmd")),
+    tar_file(deps_1st_resp, rmd_deps(rmd_1st_resp)),
+    tar_change(pdf_1st_resp, render_rmd(rmd_1st_resp), deps_1st_resp, format = "file"),
+
+    # track revisions using latexdiff
+    tar_target(ref_ori, "6c7996eb"),
+    tar_target(ref_1st, "52db17a8"),
+    tar_file(file_latexdiff, latexdiff(ref_ori, ref_1st, rmd_paper, "reviews/1st-round-diff.tex")),
+    tar_file(pdf_1st_resp_diff, render_diff(rmd_paper, file_latexdiff, ref_ori, ref_1st))
+)

### 2023-06-17 R/rmd.R
workflow: set quiet to `TRUE` in `rmarkdown::render()`

@@ -49,7 +49,7 @@ render_rmd <- function(rmd, envir = parent.frame()) {
     # read yaml header
     yaml <- rmarkdown::yaml_front_matter(rmd)
 
-    out <- rmarkdown::render(rmd, "all", envir = envir)
+    out <- rmarkdown::render(rmd, "all", envir = envir, quiet = TRUE)
 
     if (unlist(lapply(yaml$output, .subset, "keep_tex"))) {
         out <- c(out, paste0(tools::file_path_sans_ext(out[1]), ".tex"))

### 2023-06-17 R/latexdiff.R
workflow: update ref sha of paper after 1st round review

@@ -68,6 +68,7 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
         )
     ))
 
+    # make sure 'rmd' and 'diff' exists in the Git repo
     if (!file.exists(file.path(dir, rmd))) {
         stop("Failed to locate 'rmd' in the Git working tree.")
     }
@@ -81,7 +82,8 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     if (gert::git_branch_exists("new", repo = dir)) gert::git_branch_delete("new", repo = dir)
     gert::git_branch_create("new", ref_new, checkout = FALSE, repo = dir)
 
-    # extract all file dependencies for both version
+    # checkout 'new' and 'old' to extract all file dependencies for both
+    # versions
     gert::git_branch_checkout("new", repo = dir, force = TRUE)
     deps_new <- rmd_deps(file.path(dir, rmd))
     gert::git_branch_checkout("old", repo = dir, force = TRUE)
@@ -90,7 +92,8 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     # find missing files in new version
     deps_miss <- setdiff(deps_old, deps_new)
 
-    # copy missing files into another temporary folder
+    # copy missing files into another temporary folder while keeping the folder
+    # strucuture
     dir_tmp <- tempfile("latexdiff")
     dir.create(dir_tmp)
     file_tmp <- file.path(dir_tmp, fs::path_rel(deps_miss, dir))
@@ -99,12 +102,18 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     }
     stopifnot(all(file.copy(deps_miss, file_tmp, overwrite = TRUE)))
 
-    # change to newer paper branch and copy missing files back
+    # change to newer paper branch and copy missing files back so that it
+    # contains all files needed to render the diff version
     gert::git_branch_checkout("new", repo = dir, force = TRUE)
     stopifnot(all(file.copy(file_tmp, deps_miss)))
 
-    new_diff <- file.path(fs::path_abs(fs::path_rel(dirname(rmd), diff), file.path(dir, diff)), basename(diff))
+    new_diff <- file.path(
+        # get the directory path where the diff lives in the temporary folder
+        fs::path_abs(fs::path_rel(dirname(rmd), diff), file.path(dir, diff)),
+        basename(diff)
+    )
[…]

### 2023-06-17 _targets.R

@@ -18,7 +18,7 @@ list(
 
     # track revisions using latexdiff
     tar_target(ref_ori, "6c7996eb"),
-    tar_target(ref_1st, "52db17a8"),
+    tar_target(ref_1st, "ee712a3a2"),
     tar_file(file_latexdiff, latexdiff(ref_ori, ref_1st, rmd_paper, "reviews/1st-round-diff.tex")),
     tar_file(pdf_1st_resp_diff, render_diff(rmd_paper, file_latexdiff, ref_ori, ref_1st))
 )

### 2023-06-29 R/latexdiff.R
workflow: support ref in `render_rmd()`
fix

@@ -58,15 +58,7 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     }
 
     # create a temporary folder to store data
-    dir <- tempfile("latexdiff")
-    dir.create(dir)
-
-    # copy whole working directory to the temporary folder
-    stopifnot(all(
-        file.copy(list.files(all.files = TRUE, no.. = TRUE), dir,
-            recursive = TRUE, overwrite = TRUE
-        )
-    ))
+    dir <- temp_store("latexdiff")
 
     # make sure 'rmd' and 'diff' exists in the Git repo
     if (!file.exists(file.path(dir, rmd))) {
@@ -100,20 +92,19 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     if (any(!dir.exists(dirs_file_tmp <- unique(dirname(file_tmp))))) {
         dir.create(dirs_file_tmp[!dir.exists(dirs_file_tmp)], recursive = TRUE)
     }
-    stopifnot(all(file.copy(deps_miss, file_tmp, overwrite = TRUE)))
+    file_copy(deps_miss, file_tmp)
 
     # change to newer paper branch and copy missing files back so that it
     # contains all files needed to render the diff version
     gert::git_branch_checkout("new", repo = dir, force = TRUE)
-    stopifnot(all(file.copy(file_tmp, deps_miss)))
+    file_copy(file_tmp, deps_miss)
 
     new_diff <- file.path(
         # get the directory path where the diff lives in the temporary folder
         fs::path_abs(fs::path_rel(dirname(rmd), diff), file.path(dir, diff)),
         basename(diff)
     )
-    stopifnot(file.copy(file.path(dir, diff), new_diff, overwrite = TRUE))
-    fs::file_copy(file.path(dir, diff), new_diff, overwrite = TRUE)
+    file_copy(file.path(dir, diff), new_diff)
 
     old <- getwd()
     setwd(dirname(new_diff))
@@ -122,7 +113,7 @@ render_diff <- function(rmd, diff, ref_old, ref_new) {
     on.exit(setwd(old), add = TRUE)
 
     new_out <- fs::path_rel(file.path(dirname(diff), out))
-    stopifnot(file.copy(file.path(dirname(new_diff), out), new_out, overwrite = TRUE))
+    file_copy(file.path(dirname(new_diff), out), new_out)
 
     unlink(c(dir, dir_tmp), recursive = TRUE)
     new_out

### 2023-06-29 R/rmd.R

@@ -45,15 +45,50 @@ rmd_deps_img <- function(rmd) {
     path_rmd_root(f[f != ""], rmd)
 }
 
-render_rmd <- function(rmd, envir = parent.frame()) {
+render_rmd <- function(rmd, ref = NULL, envir = parent.frame()) {
+    if (fs::is_absolute_path(rmd)) {
+        stop("'rmd' should be a relative path.")
+    }
+
+    # output file name
+    nm <- tools::file_path_sans_ext(basename(rmd))
+
+    if (is.null(ref)) {
+        dir <- getwd()
+    } else {
+        if (!is.null(names(ref)) && names(ref) == "") nm <- names(ref)
+
+        # copy all data and checkout ref in a temporary directory
+        dir <- temp_store("rmd")
+        br <- basename(tempfile("branch"))
+        gert::git_branch_create(br, ref, checkout = FALSE, repo = dir)
+        gert::git_branch_checkout(br, repo = dir, force = TRUE)
+
+        # change working directory
+        old <- getwd()
+        on.exit(setwd(old), add = TRUE)
+        setwd(dir)
+        on.exit(unlink(dir, recursive = TRUE), add = TRUE)
+    }
+
+    if (!file.exists(rmd)) {
+        stop("Failed to locate 'rmd' in current working directory.")
+    }
+
     # read yaml header
     yaml <- rmarkdown::yaml_front_matter(rmd)
 
-    out <- rmarkdown::render(rmd, "all", envir = envir, quiet = TRUE)
+    # render file
+    out <- rmarkdown::render(rmd, "all", nm, envir = envir, quiet = TRUE)
 
     if (unlist(lapply(yaml$output, .subset, "keep_tex"))) {
-        out <- c(out, paste0(tools::file_path_sans_ext(out[1]), ".tex"))
+        out <- c(out, paste0(nm, ".tex"))
     }
 
-    path_rmd_root(gsub(paste0(dirname(normalizePath(rmd)), "/"), "", out, fixed = TRUE), rmd)
+    out <- path_rmd_root(gsub(paste0(dirname(normalizePath(rmd)), "/"), "", out, fixed = TRUE), rmd)
+
+    # copy the file back
+    if (!is.null(ref)) file_copy(out, old)
+
+    out
 }

### 2023-06-29 R/temp.R

@@ -1,0 +1,23 @@
+temp_store <- function(prefix = "temp") {
+    # create a temporary folder to store data
+    dir <- tempfile(prefix)
+    dir.create(dir)
+
+    # copy whole working directory to the temporary folder
+    file_copy(list.files(all.files = TRUE, no.. = TRUE), dir, recursive = TRUE)
+
+    dir
+}
+
+file_copy <- function(from, to, recursive = FALSE) {
+    res <- file.copy(from, to, overwrite = TRUE, copy.date = TRUE, recursive = recursive)
+
+    if (any(!res)) {
+        stop(sprintf(
+            "Failed to copy file: [%s]",
+            paste0("'", from[!res], "'", collapse = "\n")
+        ))
+    }
+
+    normalizePath(to)
+}

### 2023-06-29 _targets.R

@@ -6,6 +6,11 @@ tar_source("R")
 list(
     tar_target(dir_paper, "full-paper"),
 
+    # commit SHA of the original paper
+    tar_target(ref_ori, "6c7996eb"),
+    # commit SHA of the paper after response to 1st round review
+    tar_target(ref_1st, "ee712a3a2"),
+
     # render full paper
     tar_file(rmd_paper, file.path(dir_paper, "paper.Rmd")),
     tar_file(deps_paper, rmd_deps(rmd_paper)),
@@ -17,8 +22,6 @@ list(
     tar_change(pdf_1st_resp, render_rmd(rmd_1st_resp), deps_1st_resp, format = "file"),
 
     # track revisions using latexdiff
-    tar_target(ref_ori, "6c7996eb"),
-    tar_target(ref_1st, "ee712a3a2"),
     tar_file(file_latexdiff, latexdiff(ref_ori, ref_1st, rmd_paper, "reviews/1st-round-diff.tex")),
     tar_file(pdf_1st_resp_diff, render_diff(rmd_paper, file_latexdiff, ref_ori, ref_1st))
 )

### 2023-06-29 full-paper/paper.Rmd
paper: add finial version

@@
 
-date: "2023-05-27"
+date: "2023-06-29"
 id: 1612
 
-blind: true
+blind: false
 ---
@@
 
+# Acknowledgements
+
+This study was funded by Research Foundation of Chongqing University of Science
+and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041),
+The authors also thank the support from the Berkeley Education Alliance for
+Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
+Sustainability in the Tropics (SinBerBEST) Program and thank Prof. Adrian Chong
+(National University of Singapore) for his scientific input during epwshiftr
+development.
+
 # References {-}

### 2023-06-29 full-paper/paper.Rmd
latex: update Code environment setup

@@
   x <- hooks(x, options)
-  x <- ifelse(!is.null(options$code.ref), paste0("\\label{", options$code.ref, "}", x), x)
-  ifelse(!is.null(options$code.cap), paste0("\\captionof{code}{", options$code.cap, "}", x), x)
+  if (!is.null(options$code.ref)) {
+    x <- paste0("\\label{", options$code.ref, "}", x)
+  }
+  if (!is.null(options$code.cap)) {
+    x <- paste0(c(
+      "```{=latex}\n",
+      "\\begin{Code}\n",
+      "\\caption{", options$code.cap, "}\n",
+      "```\n",
+      x,
+      "```{=latex}\n",
+      "\\end{Code}\n",
+      "```"
+    ))
+  }
+  x
 })

### 2023-06-29 full-paper/paper.tex
workflow: rerender paper and diff

@@
 % add caption for codes
-\DeclareNewFloatType{code}{placement=h, fileext=code, name=Listing}
-\captionsetup[code]{aboveskip=10pt, belowskip=1pt}
+\newenvironment{Code}{\captionsetup{type=code}}{}
+\DeclareNewFloatType{Code}{placement=h, fileext=code, name=Listing}
+\DeclareFloatVCode{beforefloat}{\vspace{2pt}}
+\DeclareFloatVCode{afterfloat}{\vspace{-10pt}}
+\floatsetup[Code]{capposition=top, captionskip=1pt, precode=beforefloat, postcode=afterfloat}
 
@@
     commandchars=\\\{\},
-    fontsize=\normalsize,
+    fontsize=\small,
     numbers=left,
@@
 \author{																																														% Line 3
-    \phantom{Line 4}\\
-  \phantom{Line 5}\\
-  \phantom{Line 6}\\
-  \phantom{Line 7}\\
+     Hongyuan Jia\textsuperscript{1} ,  Baisong Ning\textsuperscript{2} \\
+  \parbox{\linewidth}{\centering%
+     \textsuperscript{1}Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
+  }
   \phantom{Line 8}\\
@@
 
-\captionof{code}{Install epwshiftr}\label{lst:install}
+\begin{Code}
+\caption{Install epwshiftr}
+
+\label{lst:install}
 
@@
 \end{Shaded}
+
+\end{Code}
 
@@
 
-\captionof{code}{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
+\begin{Code}
+\caption{Query ScenarioMIP outputs using the Query Module}
+
+\label{lst:index}
 
@@
 
-\captionof{code}{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
+\begin{Code}
+\caption{Summarize the GCM NetCDF files based on the output index}
+
+\label{lst:db}
 
@@
 
-\captionof{code}{Match the global grid points directly using an EPW file and  extract raw GCM data}\label{lst:data}
+\begin{Code}
+\caption{Match the global grid points directly using an EPW file and  extract raw GCM data}
+
+\label{lst:data}
 
@@
 
-\captionof{code}{Perform morphing and generate future EPWs}\label{lst:epw}
+\begin{Code}
+\caption{Perform morphing and generate future EPWs}
+
+\label{lst:epw}
 
@@
 
+\end{Code}
+
 Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
@@
 
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+This study was funded by Research Foundation of Chongqing University of Science
+and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
+The authors also thank the support from the Berkeley Education Alliance for
+Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
+Sustainability in the Tropics (SinBerBEST) Program and thank Prof.~Adrian Chong
+(National University of Singapore) for his scientific input during epwshiftr
+development.
+
 %here starts the references

### 2023-06-29 _targets.R

@@ -9,12 +9,14 @@ list(
     # commit SHA of the original paper
     tar_target(ref_ori, "6c7996eb"),
     # commit SHA of the paper after response to 1st round review
-    tar_target(ref_1st, "ee712a3a2"),
+    tar_target(ref_1st, "ee712a3a"),
+    # commit SHA of the final paper, NULL for current commit
+    tar_target(ref_final, NULL),
 
     # render full paper
     tar_file(rmd_paper, file.path(dir_paper, "paper.Rmd")),
     tar_file(deps_paper, rmd_deps(rmd_paper)),
-    tar_change(pdf_paper, render_rmd(rmd_paper), deps_paper, format = "file"),
+    tar_change(pdf_paper, render_rmd(rmd_paper, ref_final), deps_paper, format = "file"),
 
     # render 1st round response to reviewer comments
     tar_file(rmd_1st_resp, file.path(dir_paper, "reviews", "1st-round-resp.Rmd")),

### 2023-06-30 R/pack.R
workflow: add tex packing function and create zip bundle

@@ -1,0 +1,39 @@
+pack_tex <- function(tex, deps, name = tools::file_path_sans_ext(tex)) {
+    if (fs::is_absolute_path(tex)) {
+        stop("'tex' should be a relative path.")
+    }
+
+    if (any(fs::is_absolute_path(deps))) {
+        stop("'deps' should be all relative paths.")
+    }
+
+    # make sure tex and deps are in the same root folder
+    if ((root <- fs::path_common(c(tex, deps))) == "") {
+        stop("Please make sure 'tex' and 'deps' share the same root folder.")
+    }
+
+    zipfile <- tempfile("packtex", fileext = ".zip")
+
+    # create a temporary to store all files
+    dir <- tempfile("packtex")
+    dir.create(dir)
+
+    # get folder structure relative to root
+    dirs <- unique(dirname(c(tex, deps)))
+    dirs <- fs::path_rel(dirs, root)
+    # create folder structure
+    for (d in file.path(dir, dirs)) {
+        if (!dir.exists(d)) dir.create(d, FALSE, TRUE)
+    }
+    file_copy(c(tex, deps), file.path(dir, fs::path_rel(c(tex, deps), root)))
+
+    old <- getwd()
+    on.exit(setwd(old), add = TRUE)
+    setwd(dir)
+    zip(zipfile, ".")
+
+    out <- paste0(name, ".zip")
+    setwd(old)
+    file_copy(zipfile, out)
+    as.character(fs::path_rel(out))
+}

### 2023-06-30 _targets.R

@@ -25,5 +25,8 @@ list(
 
     # track revisions using latexdiff
     tar_file(file_latexdiff, latexdiff(ref_ori, ref_1st, rmd_paper, "reviews/1st-round-diff.tex")),
-    tar_file(pdf_1st_resp_diff, render_diff(rmd_paper, file_latexdiff, ref_ori, ref_1st))
+    tar_file(pdf_1st_resp_diff, render_diff(rmd_paper, file_latexdiff, ref_ori, ref_1st)),
+
+    # pack the final tex bundle for submission
+    tar_file(zip_paper, pack_tex(pdf_paper[tools::file_ext(pdf_paper) == "tex"], deps_paper))
 )

### 2023-09-07 full-paper/paper.Rmd
paper: update authors

@@
     affiliation: |
-        Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
+        School of Civil Engineering and Architecture, Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
+  - name: Adrian Chong
+    order: 2
+    email: adrian.chong@nus.edu.sg
+    affiliation: |
+        Department of the Built Environment, College of Design and Engineering, National University of Singapore, 117566, Singapore
   - name: Baisong Ning
-    order: 2
+    order: 3
     email: bsning@foxmail.com
     affiliation: |
-        Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China
+        School of Civil Engineering, Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China
 
@@
 Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
-Sustainability in the Tropics (SinBerBEST) Program and thank Prof. Adrian Chong
-(National University of Singapore) for his scientific input during epwshiftr
-development.
+Sustainability in the Tropics (SinBerBEST) Program.
 

### 2023-09-07 full-paper/paper.tex
paper: update authors

@@
 \author{																																														% Line 3
-     Hongyuan Jia\textsuperscript{1} ,  Baisong Ning\textsuperscript{2} \\
+     Hongyuan Jia\textsuperscript{1} ,  Adrian Chong\textsuperscript{2} ,  Baisong Ning\textsuperscript{3} \\
   \parbox{\linewidth}{\centering%
-     \textsuperscript{1}Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
+     \textsuperscript{1}School of Civil Engineering and Architecture, Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Department of the Built Environment, College of Design and Engineering, National University of Singapore, 117566, Singapore \\ \textsuperscript{3}School of Civil Engineering, Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
   }
@@
 
-\hypertarget{highlights}{%
-\section{Highlights}\label{highlights}}
+\section{Highlights}\label{highlights}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
@@
 
-\hypertarget{climate-scenarios-in-cmip6-scenariomip}{%
-\section{Climate scenarios in CMIP6 ScenarioMIP}\label{climate-scenarios-in-cmip6-scenariomip}}
+\section{Climate scenarios in CMIP6 ScenarioMIP}\label{climate-scenarios-in-cmip6-scenariomip}
 
@@
 
-\hypertarget{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}{%
-\section{\texorpdfstring{\texttt{epwshiftr}: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}{epwshiftr: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}}\label{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}}
+\section{\texorpdfstring{\texttt{epwshiftr}: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}{epwshiftr: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}}\label{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}
 
@@
 
-\hypertarget{query-scenariomip-gcm-output-using-esgf}{%
-\subsection{Query ScenarioMIP GCM output using ESGF}\label{query-scenariomip-gcm-output-using-esgf}}
+\subsection{Query ScenarioMIP GCM output using ESGF}\label{query-scenariomip-gcm-output-using-esgf}
 
@@
 
-\hypertarget{gcm-raw-output-data-management}{%
-\subsection{GCM raw output data management}\label{gcm-raw-output-data-management}}
+\subsection{GCM raw output data management}\label{gcm-raw-output-data-management}
 
@@
 
-\hypertarget{extraction-of-raw-climate-change-data-based-on-geographic-location}{%
-\subsection{Extraction of raw climate change data based on geographic location}\label{extraction-of-raw-climate-change-data-based-on-geographic-location}}
+\subsection{Extraction of raw climate change data based on geographic location}\label{extraction-of-raw-climate-change-data-based-on-geographic-location}
 
@@
 
-\hypertarget{generation-of-future-weather-data-using-morphing-statistical-downscaling}{%
-\subsection{Generation of future weather data using morphing statistical downscaling}\label{generation-of-future-weather-data-using-morphing-statistical-downscaling}}
+\subsection{Generation of future weather data using morphing statistical downscaling}\label{generation-of-future-weather-data-using-morphing-statistical-downscaling}
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\section{Conclusion}\label{conclusion}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
-Sustainability in the Tropics (SinBerBEST) Program and thank Prof.~Adrian Chong
-(National University of Singapore) for his scientific input during epwshiftr
-development.
+Sustainability in the Tropics (SinBerBEST) Program.
 

### 2024-01-03 full-paper/paper.Rmd
paper: fix typos and grammar problems

@@
 However, morphing may under- or overestimate climate change impacts because of
-the lacking of ability to capture future extreme weather conditions and
+the lack of ability to capture future extreme weather conditions and
 potential differences in the reference time frame of the TMY and GCM data
@@
 [@dickinson2016generating], and Meteonorm [@remund2020meteonorm] are three
-future weather generators widely used in literature. CCWorldWeatherGen provides
+future weather generators widely used in the literature. CCWorldWeatherGen provides
 a graphical interface based on Microsoft Excel to generate weather files in EPW
@@
 Assessment Report (AR5). At the same time, both are commercial products, and the
-weather data under a single climate scenario often cost hundreds of dollars.
+weather data under a single climate scenario often costs hundreds of dollars.
 
@@
 single climate scenario can reach more than 1 GB. The CMIP6 ScenarioMIP contains
-dozens of different GCMs, and the total size of all output files will get more
+dozens of different GCMs, and the total size of all output files will be more
 than 10 TB, making it impossible to download all of them for analysis.
@@
 conditions, providing download links of NetCDF files. The query result will be
-processed into a data frame that contains 22 metadata that describes each
+processed into a data frame that contains 22 metadata describing each
 output. Also, an output index is generated based on the query to
@@
   continuing. Moreover, the morphing method will use the shift factor ($\Delta x$)
-  to to avoid unrealistic morphed values.
+  to avoid unrealistic morphed values.
 
@@
 interface provides parameters to modify which factors should be used for each
-meteorological variable, with meaningful defaults value given. For example,
+meteorological variable, with meaningful default values given. For example,
 radiation-related variables are, by default, morphed using the stretch factor,
@@
 
-This study was funded by Research Foundation of Chongqing University of Science
-and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041),
+This study was funded by the Research Foundation of Chongqing University of Science
+and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041).
 The authors also thank the support from the Berkeley Education Alliance for

### 2024-01-03 full-paper/paper.tex
paper: rebuild tex and zip

@@
 \citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
-future weather generators widely used in literature. CCWorldWeatherGen provides
+future weather generators widely used in the literature. CCWorldWeatherGen provides
 a graphical interface based on Microsoft Excel to generate weather files in EPW
@@
   continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
-  to to avoid unrealistic morphed values.
+  to avoid unrealistic morphed values.
 \end{itemize}
@@
 
-This study was funded by Research Foundation of Chongqing University of Science
-and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
+This study was funded by the Research Foundation of Chongqing University of Science
+and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041).
 The authors also thank the support from the Berkeley Education Alliance for
